### 2014-12-11 paper/paper.tex
added paper draft and kinetic energy containers

\documentclass[aps,prl,floatfix,preprint,nofootinbib]{revtex4}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epsfig}
\begin{document}
\title{Modeling Two Body Collisions with Spring Potential Interactions}
\author{Matthew Epland, Douglas Davis}
\affiliation{Department of Physics, Duke University}
\date{\today}
\begin{abstract}
  This report describes a computational study of two body collisions where the dynamics of the bodies are governed by a Hooke's Law type force at the interaction points. We investigate a number of scenarios which involve a stationary target object which is contacted by a projectile object with some horizontal velocity in a two dimensional plane. Object trajectories are determined from a simulation software package, along with other various kinematic variables. Parameters governing the interactions and the kinematics are changed to study various trends in the kinematic variables for different scenarios.
\end{abstract}\maketitle
\section{yar}
this is cool.
\end{document}

### 2014-12-11 main.cpp

@@ -85,6 +85,12 @@ int main(int argc, char *argv[])
   std::vector<double> CM_y_vector;
   std::vector<double> CM_vx_vector;
   std::vector<double> CM_vy_vector;
+  std::vector<double> target_KE_vector;
+  std::vector<double> projectile_KE_vector;
+  std::vector<double> total_KE_vector;
+  projectile_KE_vector.push_back(0.5*projectile_mass*projectile_vx0*projectile_vx0);
+  target_KE_vector.push_back(0.0);
+  total_KE_vector.push_back(projectile_KE_vector.at(0)+target_KE_vector.at(0));
   CM_x_vector.push_back((initial_kinvec1.x()*target_mass + initial_kinvec2.x()*projectile_mass)/(projectile_mass+target_mass));
   CM_y_vector.push_back((initial_kinvec1.y()*target_mass + initial_kinvec2.y()*projectile_mass)/(projectile_mass+target_mass));
   CM_vx_vector.push_back((initial_kinvec1.vx()*target_mass + initial_kinvec2.vx()*projectile_mass)/(projectile_mass+target_mass));
@@ -140,6 +146,11 @@ int main(int argc, char *argv[])
     new_kv2.set_vx((1-eta)*p2.kinvecs().at(i-1).vx() + Fmag*Fx*delta_t/projectile_mass);
     new_kv2.set_vy((1-eta)*p2.kinvecs().at(i-1).vy() + Fmag*Fy*delta_t/projectile_mass);
 
+    auto current_KE_1 = .5*target_mass*(std::pow(new_kv1.vx(),2) + std::pow(new_kv1.vy(),2));
+    auto current_KE_2 = .5*projectile_mass*(std::pow(new_kv2.vx(),2) + std::pow(new_kv2.vy(),2));
+    target_KE_vector.push_back(current_KE_1);
+    projectile_KE_vector.push_back(current_KE_2);
+    total_KE_vector.push_back(current_KE_1+current_KE_2);
 
     // __ center of mass
     CM_x_vector.push_back((p1.kinvecs().at(i-1).x()*target_mass + p2.kinvecs().at(i-1).x()*projectile_mass)/(projectile_mass+target_mass));

### 2014-12-11 main.cpp
added cases

@@ -30,10 +30,11 @@ int main(int argc, char *argv[])
     ("t-mass",   po::value<double>()->default_value(5.000),"target mass")
     ("p-vinit",  po::value<double>()->default_value(5.000),"projectile initial velocity")
     ("delta-t,t",po::value<double>()->default_value(0.001),"time step")
-    ("impact,s", po::value<double>()->default_value(1.000),"impact parameter")
-    ("spring,k", po::value<double>()->default_value(1.000),"spring constant")
+    ("impact,s", po::value<double>()->default_value(2.000),"impact parameter")
+    ("spring,k", po::value<double>()->default_value(100.0),"spring constant")
     ("eta,e",    po::value<double>()->default_value(0.000),"energy disipation")
-    ("lambda,l", po::value<double>()->default_value(1.000),"power law");
+    ("lambda,l", po::value<double>()->default_value(1.000),"power law")
+    ("case,c", po::value<int>()->default_value(0),"case selection\n0  defaults\n1  hard k, off center\n2  hard k, on center\n3  soft k, off center\n4  soft k, on center\n5  hard k, equal balls, on center");
 
   po::variables_map vm;
   po::store(po::parse_command_line(argc,argv,desc),vm);
@@ -45,7 +46,7 @@ int main(int argc, char *argv[])
   }
     
   double delta_t           = vm["delta-t"].as<double>();
-  double max_frac_Dx	   = 0.01; // Largest allowed change in position per timestep
+  double max_frac_Dx	   = 0.01; // largest allowed change in position per timestep
 
   double projectile_mass   = vm["p-mass"].as<double>();
   double projectile_radius = vm["p-radius"].as<double>();
@@ -56,12 +57,30 @@ int main(int argc, char *argv[])
   double target_x0         = 1.00; // initial x position of the target
   double target_y0         = 0.00; // initial y position of the target
   
-  double impact_paramter   = vm["impact"].as<double>();
+  double impact_parameter   = vm["impact"].as<double>();
 
   double K      = vm["spring"].as<double>();               // spring constant
   double Lambda = vm["lambda"].as<double>();               // force power law
-  double eta    = vm["eta"].as<double>();               // energy disapation parameter (0 = none) (fraction loss/time step)
[…]

### 2014-12-11 main.cpp
pushing some kinetic/potential energy stuff and leaving mac

@@ -67,19 +67,19 @@ int main(int argc, char *argv[])
 
   if(my_case != 0){
     if(my_case == 1)
-	K = 100.0, impact_parameter = (2/3)*target_radius;
+      K = 100.0, impact_parameter = (2/3)*target_radius;
     if(my_case == 2)
-        K = 100.0, impact_parameter = 0;
+      K = 100.0, impact_parameter = 0;
     if(my_case == 3)
-        K = 10.0,  impact_parameter = (2/3)*target_radius;
+      K = 10.0,  impact_parameter = (2/3)*target_radius;
     if(my_case == 4)
-        K = 10.0,  impact_parameter = 0;
+      K = 10.0,  impact_parameter = 0;
     if(my_case == 5)
-        K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 5.00, projectile_mass = 5.00, impact_parameter = 0.00;
-    }
-    else{
-	std::cout << "case parameter out of bounds, using defaults" << std::endl;
-    }
+      K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 5.00, projectile_mass = 5.00, impact_parameter = 0.00;
+  }
+  else{
+    std::cout << "case parameter out of bounds, using defaults" << std::endl;
+  }
 
   particle p1(target_mass,target_radius);
   particle p2(projectile_mass,projectile_radius);
@@ -108,6 +108,8 @@ int main(int argc, char *argv[])
   std::vector<double> target_KE_vector;
   std::vector<double> projectile_KE_vector;
   std::vector<double> total_KE_vector;
+  std::vector<double> PE_vector;
+  PE_vector.push_back(0.0);
   projectile_KE_vector.push_back(0.5*projectile_mass*projectile_vx0*projectile_vx0);
   target_KE_vector.push_back(0.0);
   total_KE_vector.push_back(projectile_KE_vector.at(0)+target_KE_vector.at(0));
@@ -166,12 +168,15 @@ int main(int argc, char *argv[])
     new_kv2.set_vx((1-eta)*p2.kinvecs().at(i-1).vx() + Fmag*Fx*delta_t/projectile_mass);
[…]

### 2014-12-11 main.cpp
small changes

@@ -76,9 +76,8 @@ int main(int argc, char *argv[])
       K = 10.0,  impact_parameter = 0;
     if(my_case == 5)
       K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 5.00, projectile_mass = 5.00, impact_parameter = 0.00;
-  }
-  else{
-    std::cout << "case parameter out of bounds, using defaults" << std::endl;
+    else
+      std::cout << "case parameter out of bounds, using defaults" << std::endl;
   }
 
   particle p1(target_mass,target_radius);
@@ -457,6 +456,8 @@ int main(int argc, char *argv[])
   c6->Print("out/Fmag_vs_t.pdf", "Portrait pdf");
 
 
+  // Energy Graph
+
   TCanvas *c7 = new TCanvas("c7","",600,600);
   TGraph *PE_tg  = new TGraph(PE_vector.size(),&time_vector[0],&PE_vector[0]);
   TGraph *KE_p1  = new TGraph(target_KE_vector.size(),&time_vector[0],&target_KE_vector[0]);
@@ -478,16 +479,18 @@ int main(int argc, char *argv[])
   mgKE->Add(KE_p1);
   mgKE->Add(KE_p2);
   mgKE->Add(KE_tot);
+  mgKE->Draw("AP");
+
+  mgKE->GetXaxis()->SetTitle("t");
+  mgKE->GetYaxis()->SetTitle("Energy");
 
   TLegend* mgKEleg = new TLegend(0.73,0.5-0.075,0.98,0.5+0.075);
   mgKEleg->AddEntry(PE_tg,"Potential","p");
   mgKEleg->AddEntry(KE_p2,"KE Projectile","p");
   mgKEleg->AddEntry(KE_p1,"KE Target","p");
   mgKEleg->AddEntry(KE_tot,"KE Total","p");
-  mgKE->Draw("AP");
-  mgKE->GetXaxis()->SetTitle("t");
-  mgKE->GetYaxis()->SetTitle("Energy");
   mgKEleg->Draw("same");
+
   gPad->Modified();
   c7->Print("out/KE_vs_t.pdf","Portrait pdf");
   

### 2014-12-11 main.cpp
fixed PE draw

@@ -464,7 +464,7 @@ int main(int argc, char *argv[])
   TGraph *KE_p2  = new TGraph(projectile_KE_vector.size(),&time_vector[0],&projectile_KE_vector[0]);
   TGraph *KE_tot = new TGraph(total_KE_vector.size(),&time_vector[0],&total_KE_vector[0]);
 
-  PE_tg->SetMarkerColor(7);
+  PE_tg->SetMarkerStyle(7);
   KE_p1->SetMarkerStyle(7);
   KE_p2->SetMarkerStyle(7);
   KE_tot->SetMarkerStyle(7);

### 2014-12-11 main.cpp
formattting

@@ -34,7 +34,7 @@ int main(int argc, char *argv[])
     ("spring,k", po::value<double>()->default_value(100.0),"spring constant")
     ("eta,e",    po::value<double>()->default_value(0.000),"energy disipation")
     ("lambda,l", po::value<double>()->default_value(1.000),"power law")
-    ("case,c", po::value<int>()->default_value(0),"case selection\n0  defaults\n1  hard k, off center\n2  hard k, on center\n3  soft k, off center\n4  soft k, on center\n5  hard k, equal balls, on center");
+    ("case,c",   po::value<int>()->default_value(0),"case selection\n0  defaults\n1  hard k, off center\n2  hard k, on center\n3  soft k, off center\n4  soft k, on center\n5  hard k, equal balls, on center");
 
   po::variables_map vm;
   po::store(po::parse_command_line(argc,argv,desc),vm);
@@ -54,27 +54,24 @@ int main(int argc, char *argv[])
   
   double target_mass       = vm["t-mass"].as<double>();
   double target_radius     = vm["t-radius"].as<double>();
-  double target_x0         = 1.00; // initial x position of the target
-  double target_y0         = 0.00; // initial y position of the target
-  
-  double impact_parameter   = vm["impact"].as<double>();
+  double target_x0         = 1.00;                                    // initial x position of the target
+  double target_y0         = 0.00;                                    // initial y position of the target
+  double impact_parameter  = vm["impact"].as<double>();               // self explanatory
+  double K                 = vm["spring"].as<double>();               // spring constant
+  double Lambda            = vm["lambda"].as<double>();               // force power law
+  double eta               = vm["eta"].as<double>();                  // energy disapation parameter (0 = none) (fraction loss/time step)
+  double my_case           = vm["case"].as<int>();                    // case selection
 
-  double K      = vm["spring"].as<double>();               // spring constant
[…]

### 2014-12-11 main.cpp
finalized E vs t graph

@@ -15,8 +15,16 @@
 #include "TLegend.h"
 #include "TLatex.h"
 #include "TEllipse.h"
+#include "TStyle.h"
+#include "TPaveStats.h"
 
 #include "boost/program_options.hpp"
+
+Double_t flat_fit(Double_t *v, Double_t *par)
+{
+  return par[0];
+}
+
 
 int main(int argc, char *argv[])
 {
@@ -172,7 +180,7 @@ int main(int argc, char *argv[])
     projectile_KE_vector.push_back(current_KE_2);
     total_KE_vector.push_back(current_KE_1+current_KE_2);
 
-    double current_PE = K*std::pow(std::fabs((target_radius+projectile_radius)-separation),Lambda+1)/Lambda;
+    double current_PE = K*std::pow(std::fabs((target_radius+projectile_radius)-separation),Lambda+1)/(Lambda+1);
     PE_vector.push_back(current_PE);
 
     Etot_vector.push_back(current_PE+current_KE_1+current_KE_2);
@@ -457,8 +465,8 @@ int main(int argc, char *argv[])
 
 
   // Energy Graph
-
-  TCanvas *c7 = new TCanvas("c7","",600,600);
+  TCanvas *c7 = new TCanvas("c7","",800,600);
+  gPad->SetRightMargin(.20);
 
   TGraph *PE_tg  = new TGraph(PE_vector.size(),&time_vector[0],&PE_vector[0]);
   TGraph *KE_p1  = new TGraph(target_KE_vector.size(),&time_vector[0],&target_KE_vector[0]);
@@ -478,27 +486,47 @@ int main(int argc, char *argv[])
   KE_tot->SetMarkerColor(kGreen);
   E_tot->SetMarkerColor(kCyan);
   
-  TMultiGraph *mgKE = new TMultiGraph();
-  mgKE->Add(PE_tg);
-  mgKE->Add(KE_p1);
-  mgKE->Add(KE_p2);
-  mgKE->Add(KE_tot);
-  mgKE->Add(E_tot);
-  mgKE->Draw("AP");
+  TMultiGraph *mgE = new TMultiGraph();
+  mgE->Add(PE_tg);
+  mgE->Add(KE_p1);
+  mgE->Add(KE_p2);
+  mgE->Add(KE_tot);
+  mgE->Add(E_tot);
[…]

### 2014-12-11 main.cpp
started python program to read output of list of single event params

@@ -25,6 +25,27 @@ Double_t flat_fit(Double_t *v, Double_t *par)
   return par[0];
 }
 
+void print_single_stat(double tm, double tr, double pm, double pr, double dt, double pvx0, double ip, double k, double eta, double L, double ms, double fvxt, double fvyt, double fvt, double fvxp, double fvyp, double fvp)
+{
+  std::cout << tm   << "\t"
+	    << tr   << "\t"
+	    << pm   << "\t"
+	    << pr   << "\t"
+	    << dt   << "\t"
+	    << pvx0 << "\t"
+	    << ip   << "\t"
+	    << k    << "\t"
+	    << eta  << "\t"
+	    << L    << "\t"
+	    << ms   << "\t"
+	    << fvxt << "\t"
+	    << fvyt << "\t"
+	    << fvt  << "\t"
+	    << fvxp << "\t"
+	    << fvyp << "\t"
+	    << fvp  << "\t"
+	    << std::endl;
+}
 
 int main(int argc, char *argv[])
 {
@@ -527,6 +548,15 @@ int main(int argc, char *argv[])
   gPad->Update();
   gPad->Modified();
   c7->Print("out/E_vs_t.pdf","Portrait pdf");
+
+  // void print_single_stat(double tm, double tr, double pm, double pr, double dt, double pvx0, double ip, double k, double eta, double L, double ms, double fvxt, double fvyt, double fvt, double fvxp, double fvyp, double fvp)
+
+  print_single_stat(target_mass, target_radius, projectile_mass, projectile_radius,
+		    delta_t, projectile_vx0, impact_parameter, K, eta, Lambda, min_sep,
+		    p1.kinvecs().at(p1.kinvecs().size()-1).vx(),p1.kinvecs().at(p1.kinvecs().size()-1).vy(),
+		    std::sqrt(std::pow(p1.kinvecs().at(p1.kinvecs().size()-1).vx(),2)+std::pow(p1.kinvecs().at(p1.kinvecs().size()-1).vy(),2)),
+		    p2.kinvecs().at(p2.kinvecs().size()-1).vx(),p2.kinvecs().at(p2.kinvecs().size()-1).vy(),
+		    std::sqrt(std::pow(p2.kinvecs().at(p2.kinvecs().size()-1).vx(),2)+std::pow(p2.kinvecs().at(p2.kinvecs().size()-1).vy(),2)));
   
   return 0;
 }

### 2014-12-11 python/otherplots.py

@@ -1,0 +1,20 @@
+#!/usr/bin/env python2
+
+import ROOT
+import numpy as np
+
+data = np.loadtxt('data.dat')
+tm, tr, pm, pr, dt, pvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp = data.T
+
+print ms
+print ip
+
+ms_vs_ip = ROOT.TGraph()
+i = 0
+for m,n in zip(ms,ip):
+    ms_vs_ip.SetPoint(i,m,n)
+    i = i + 1
+ms_vs_ip.SetMarkerStyle(7)
+ms_vs_ip.Draw('AP')
+
+raw_input('')

### 2014-12-11 main.cpp
progress

@@ -192,8 +192,8 @@ int main(int argc, char *argv[])
     new_kv2.set_x(p2.kinvecs().at(i-1).x() + p2.kinvecs().at(i-1).vx()*delta_t + 0.5*Fmag*Fx*delta_t*delta_t/projectile_mass);
     new_kv2.set_y(p2.kinvecs().at(i-1).y() + p2.kinvecs().at(i-1).vy()*delta_t + 0.5*Fmag*Fy*delta_t*delta_t/projectile_mass);
 
-    new_kv2.set_vx((1-eta)*p2.kinvecs().at(i-1).vx() + Fmag*Fx*delta_t/projectile_mass);
-    new_kv2.set_vy((1-eta)*p2.kinvecs().at(i-1).vy() + Fmag*Fy*delta_t/projectile_mass);
+    new_kv2.set_vx((1.0-eta)*p2.kinvecs().at(i-1).vx() + Fmag*Fx*delta_t/projectile_mass);
+    new_kv2.set_vy((1.0-eta)*p2.kinvecs().at(i-1).vy() + Fmag*Fy*delta_t/projectile_mass);
 
     double current_KE_1 = .5*target_mass*(std::pow(new_kv1.vx(),2) + std::pow(new_kv1.vy(),2));
     double current_KE_2 = .5*projectile_mass*(std::pow(new_kv2.vx(),2) + std::pow(new_kv2.vy(),2));
@@ -522,6 +522,7 @@ int main(int argc, char *argv[])
   TF1* flat_fit_func = new TF1("fit",flat_fit,mgE->GetXaxis()->GetXmin(),mgE->GetXaxis()->GetXmax(),1);
   flat_fit_func->SetParNames("E_{ave}");
   flat_fit_func->SetLineColor(kBlack);
+  flat_fit_func->SetLineStyle(7);
 
   E_tot->Fit("fit","q"); // Don't print stats so we can pipe the output nicely
 

### 2014-12-11 python/otherplots.py

@@ -2,19 +2,20 @@
 
 import ROOT
 import numpy as np
+import sys
 
-data = np.loadtxt('data.dat')
+data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp = data.T
 
 print ms
-print ip
+print eta
 
-ms_vs_ip = ROOT.TGraph()
+ms_vs_eta = ROOT.TGraph()
 i = 0
-for m,n in zip(ms,ip):
-    ms_vs_ip.SetPoint(i,m,n)
+for m,n in zip(ms,eta):
+    ms_vs_eta.SetPoint(i,m,n)
     i = i + 1
-ms_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.Draw('AP')
+ms_vs_eta.SetMarkerStyle(7)
+ms_vs_eta.Draw('AP')
 
 raw_input('')

### 2014-12-11 runsome.py

@@ -1,0 +1,8 @@
+#!/usr/bin/env python2
+
+import subprocess
+
+cur = 0.001
+for i in xrange(100):
+    subprocess.call("./main -e "+str(cur)+" >> data.dat",shell=True)
+    cur = cur + 0.0002

### 2014-12-11 main.cpp
added initial target velocity

@@ -25,7 +25,8 @@ Double_t flat_fit(Double_t *v, Double_t *par)
   return par[0];
 }
 
-void print_single_stat(double tm, double tr, double pm, double pr, double dt, double pvx0, double ip, double k, double eta, double L, double ms, double fvxt, double fvyt, double fvt, double fvxp, double fvyp, double fvp)
+void print_single_stat(double tm, double tr, double pm, double pr, double dt, double pvx0, double tvx0,
+		       double ip, double k, double eta, double L, double ms, double fvxt, double fvyt, double fvt, double fvxp, double fvyp, double fvp)
 {
   std::cout << tm   << "\t"
 	    << tr   << "\t"
@@ -33,6 +34,7 @@ void print_single_stat(double tm, double tr, double pm, double pr, double dt, do
 	    << pr   << "\t"
 	    << dt   << "\t"
 	    << pvx0 << "\t"
+	    << tvx0 << "\t"
 	    << ip   << "\t"
 	    << k    << "\t"
 	    << eta  << "\t"
@@ -58,6 +60,7 @@ int main(int argc, char *argv[])
     ("p-mass",   po::value<double>()->default_value(1.000),"projectile mass")
     ("t-mass",   po::value<double>()->default_value(5.000),"target mass")
     ("p-vinit",  po::value<double>()->default_value(5.000),"projectile initial velocity")
+    ("t-vinit",  po::value<double>()->default_value(0.000),"target initial velocity")
     ("delta-t,t",po::value<double>()->default_value(0.001),"time step")
     ("impact,s", po::value<double>()->default_value(2.000),"impact parameter")
     ("spring,k", po::value<double>()->default_value(100.0),"spring constant")
@@ -83,8 +86,10 @@ int main(int argc, char *argv[])
   
   double target_mass       = vm["t-mass"].as<double>();
   double target_radius     = vm["t-radius"].as<double>();
+  double target_vx0        = vm["t-vinit"].as<double>();              // initial velocity of target
   double target_x0         = 1.00;                                    // initial x position of the target
-  double target_y0         = 0.00;                                    // initial y position of the target
+  double target_y0         = 0.00;                                    // initial y position of the target_x0
+  
[…]

### 2014-12-11 python/otherplots.py

@@ -5,7 +5,7 @@ import numpy as np
 import sys
 
 data = np.loadtxt(sys.argv[1])
-tm, tr, pm, pr, dt, pvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp = data.T
+tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp = data.T
 
 print ms
 print eta

### 2014-12-11 main.cpp
fixed E0, added new cases

@@ -66,7 +66,7 @@ int main(int argc, char *argv[])
     ("spring,k", po::value<double>()->default_value(100.0),"spring constant")
     ("eta,e",    po::value<double>()->default_value(0.000),"energy disipation")
     ("lambda,l", po::value<double>()->default_value(1.000),"power law")
-    ("case,c",   po::value<int>()->default_value(0),"case selection\n0  defaults\n1  hard k, off center\n2  hard k, on center\n3  soft k, off center\n4  soft k, on center\n5  hard k, equal balls, on center");
+    ("case,c",   po::value<int>()->default_value(0),"case selection\n0  defaults\n1  hard k, off center\n2  hard k, on center\n3  soft k, off center\n4  soft k, on center\n5  hard k, equal balls, on center\n6  same balls, hard k, p_tot = 0\n7  big target coming at projectile, hard k");
 
   po::variables_map vm;
   po::store(po::parse_command_line(argc,argv,desc),vm);
@@ -107,6 +107,10 @@ int main(int argc, char *argv[])
       K = 10.0,  impact_parameter = 0;
     if ( my_case == 5 )
       K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 5.00, projectile_mass = 5.00, impact_parameter = 0.00;
+    if ( my_case == 6 )
+      K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 3.00, projectile_mass = 3.00, impact_parameter = 0.00, projectile_vx0 = 5.00, target_vx0 = -5.00;
+    if ( my_case == 7 )
+      K = 1000.0, target_radius = 3.00, projectile_radius = 1.00, target_mass = 15.00, projectile_mass = 1.00, impact_parameter = 0.00, projectile_vx0 = 1.00, target_vx0 = -5.00;
     else
       std::cout << "case parameter out of bounds, using defaults" << std::endl;
   }
@@ -142,7 +146,7 @@ int main(int argc, char *argv[])
   std::vector<double> Etot_vector;
   PE_vector.push_back(0.0);
   projectile_KE_vector.push_back(0.5*projectile_mass*projectile_vx0*projectile_vx0);
-  target_KE_vector.push_back(0.0);
+  target_KE_vector.push_back(0.5*target_mass*target_vx0*target_vx0);
   total_KE_vector.push_back(projectile_KE_vector.at(0)+target_KE_vector.at(0));
[…]

### 2014-12-12 main.cpp
adding total time steps

@@ -26,7 +26,7 @@ Double_t flat_fit(Double_t *v, Double_t *par)
 }
 
 void print_single_stat(double tm, double tr, double pm, double pr, double dt, double pvx0, double tvx0,
-		       double ip, double k, double eta, double L, double ms, double fvxt, double fvyt, double fvt, double fvxp, double fvyp, double fvp)
+		       double ip, double k, double eta, double L, double ms, double fvxt, double fvyt, double fvt, double fvxp, double fvyp, double fvp, int tts)
 {
   std::cout << tm   << "\t"
 	    << tr   << "\t"
@@ -46,6 +46,7 @@ void print_single_stat(double tm, double tr, double pm, double pr, double dt, do
 	    << fvxp << "\t"
 	    << fvyp << "\t"
 	    << fvp  << "\t"
+	    << tts  << "\t"
 	    << std::endl;
 }
 
@@ -182,7 +183,6 @@ int main(int argc, char *argv[])
     Fy = ( p2.kinvecs().at(i-1).y() - p1.kinvecs().at(i-1).y() ) / separation;
     // ( k * sqrt[ r1 + r2 - separation ]^(lambda) = k*displacement_from_equilbrium raised to lambda
     Fmag = K*std::pow(((p1.radius() + p2.radius()) - separation),Lambda);
-    
     kinvec new_kv1;
     kinvec new_kv2;
 
@@ -557,10 +557,11 @@ int main(int argc, char *argv[])
 
   print_single_stat(target_mass, target_radius, projectile_mass, projectile_radius,
 		    delta_t, projectile_vx0, target_vx0, impact_parameter, K, eta, Lambda, min_sep,
-		    p1.kinvecs().at(p1.kinvecs().size()-1).vx(),p1.kinvecs().at(p1.kinvecs().size()-1).vy(),
-		    std::sqrt(std::pow(p1.kinvecs().at(p1.kinvecs().size()-1).vx(),2)+std::pow(p1.kinvecs().at(p1.kinvecs().size()-1).vy(),2)),
-		    p2.kinvecs().at(p2.kinvecs().size()-1).vx(),p2.kinvecs().at(p2.kinvecs().size()-1).vy(),
[…]

### 2014-12-12 python/otherplots.py

@@ -5,17 +5,24 @@ import numpy as np
 import sys
 
 data = np.loadtxt(sys.argv[1])
-tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp = data.T
+tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-print ms
-print eta
-
-ms_vs_eta = ROOT.TGraph()
+dx_vs_L = ROOT.TGraph()
+ms_vs_L = ROOT.TGraph()
 i = 0
-for m,n in zip(ms,eta):
-    ms_vs_eta.SetPoint(i,m,n)
+for m,n in zip(ms,L):
+    dx_vs_L.SetPoint(i,tr[0]+pr[0]-m,n)
+    ms_vs_L.SetPoint(i,m,n)
     i = i + 1
-ms_vs_eta.SetMarkerStyle(7)
-ms_vs_eta.Draw('AP')
+
+dx_vs_L.SetMarkerStyle(7)
+ms_vs_L.SetMarkerStyle(7)
+ms_vs_L.SetMarkerColor(ROOT.kRed)
+
+mg = ROOT.TMultiGraph()
+#mg.Add(ms_vs_L)
+mg.Add(dx_vs_L)
+
+mg.Draw('AP')
 
 raw_input('')

### 2014-12-12 runsome.py

@@ -2,7 +2,7 @@
 
 import subprocess
 
-cur = 0.001
+cur = .5
 for i in xrange(100):
-    subprocess.call("./main -e "+str(cur)+" >> data.dat",shell=True)
-    cur = cur + 0.0002
+    subprocess.call("./main -c 6 -l "+str(cur)+" >> data.dat",shell=True)
+    cur = cur + 0.025

### 2014-12-12 main.cpp
fixed else ifs

@@ -100,17 +100,17 @@ int main(int argc, char *argv[])
   if ( my_case != 0 ) {
     if ( my_case == 1 )
       K = 100.0, impact_parameter = (2/3)*target_radius;
-    if ( my_case == 2 )
+    else if ( my_case == 2 )
       K = 100.0, impact_parameter = 0;
-    if ( my_case == 3 )
+    else if ( my_case == 3 )
       K = 10.0,  impact_parameter = (2/3)*target_radius;
-    if ( my_case == 4 )
+    else if ( my_case == 4 )
       K = 10.0,  impact_parameter = 0;
-    if ( my_case == 5 )
+    else if ( my_case == 5 )
       K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 5.00, projectile_mass = 5.00, impact_parameter = 0.00;
-    if ( my_case == 6 )
+    else if ( my_case == 6 )
       K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 3.00, projectile_mass = 3.00, impact_parameter = 0.00, projectile_vx0 = 5.00, target_vx0 = -5.00;
-    if ( my_case == 7 )
+    else if ( my_case == 7 )
       K = 1000.0, target_radius = 3.00, projectile_radius = 1.00, target_mass = 15.00, projectile_mass = 1.00, impact_parameter = 0.00, projectile_vx0 = 1.00, target_vx0 = -5.00;
     else
       std::cout << "case parameter out of bounds, using defaults" << std::endl;

### 2014-12-12 python/runsome.py
moving to lninux

@@ -2,7 +2,9 @@
 
 import subprocess
 
+default_settings='--p-radius 1 --t-radius 2 --p-mass 0.25 --t-mass 2 -s 1'
+
 cur = .5
 for i in xrange(100):
-    subprocess.call("./main -c 6 -l "+str(cur)+" >> data.dat",shell=True)
+    subprocess.call("./main "+str(default_settings)+" -l "+str(cur)+" >> data.dat",shell=True)
     cur = cur + 0.025

### 2014-12-12 python/otherplots.py
leaving the office time to go home

@@ -7,21 +7,20 @@ import sys
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_L = ROOT.TGraph()
-ms_vs_L = ROOT.TGraph()
+dx_vs_ip = ROOT.TGraph()
+ms_vs_ip = ROOT.TGraph()
 i = 0
-for m,n in zip(ms,L):
-    dx_vs_L.SetPoint(i,tr[0]+pr[0]-m,n)
-    ms_vs_L.SetPoint(i,m,n)
+for m,n in zip(ms,ip):
+    dx_vs_ip.SetPoint(i,n,tr[0]+pr[0]-m)
+    ms_vs_ip.SetPoint(i,n,m)
     i = i + 1
 
-dx_vs_L.SetMarkerStyle(7)
-ms_vs_L.SetMarkerStyle(7)
-ms_vs_L.SetMarkerColor(ROOT.kRed)
+dx_vs_ip.SetMarkerStyle(7)
+ms_vs_ip.SetMarkerStyle(7)
+ms_vs_ip.SetMarkerColor(ROOT.kRed)
 
 mg = ROOT.TMultiGraph()
-#mg.Add(ms_vs_L)
-mg.Add(dx_vs_L)
+mg.Add(dx_vs_ip)
 
 mg.Draw('AP')
 

### 2014-12-12 python/runsome.py

@@ -2,9 +2,9 @@
 
 import subprocess
 
-default_settings='--p-radius 1 --t-radius 2 --p-mass 0.25 --t-mass 2 -s 1'
+default_settings='--p-radius 1 --t-radius 2 --p-mass 0.25 --t-mass 2 --delta-t .0001'
 
-cur = .5
+cur = 0
 for i in xrange(100):
-    subprocess.call("./main "+str(default_settings)+" -l "+str(cur)+" >> data.dat",shell=True)
-    cur = cur + 0.025
+    subprocess.call("./main "+str(default_settings)+" -s "+str(cur)+" >> data.dat",shell=True)
+    cur = cur+.02

### 2014-12-12 python/variable_eta.py
setting up for python plots

@@ -1,0 +1,27 @@
+#!/usr/bin/env python2
+
+import ROOT
+import numpy as np
+import sys
+
+data = np.loadtxt(sys.argv[1])
+tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
+
+dx_vs_ip = ROOT.TGraph()
+ms_vs_ip = ROOT.TGraph()
+i = 0
+for m,n in zip(ms,ip):
+    dx_vs_ip.SetPoint(i,n,tr[0]+pr[0]-m)
+    ms_vs_ip.SetPoint(i,n,m)
+    i = i + 1
+
+dx_vs_ip.SetMarkerStyle(7)
+ms_vs_ip.SetMarkerStyle(7)
+ms_vs_ip.SetMarkerColor(ROOT.kRed)
+
+mg = ROOT.TMultiGraph()
+mg.Add(dx_vs_ip)
+
+mg.Draw('AP')
+
+raw_input('')

### 2014-12-12 python/variable_L.py
ya

@@ -7,20 +7,20 @@ import sys
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_ip = ROOT.TGraph()
-ms_vs_ip = ROOT.TGraph()
+dx_vs_L = ROOT.TGraph()
+ms_vs_L = ROOT.TGraph()
 i = 0
-for m,n in zip(ms,ip):
-    dx_vs_ip.SetPoint(i,n,tr[0]+pr[0]-m)
-    ms_vs_ip.SetPoint(i,n,m)
+for m,n in zip(ms,L):
+    dx_vs_L.SetPoint(i,n,tr[0]+pr[0]-m)
+    ms_vs_L.SetPoint(i,n,m)
     i = i + 1
 
-dx_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerColor(ROOT.kRed)
+dx_vs_L.SetMarkerStyle(7)
+ms_vs_L.SetMarkerStyle(7)
+ms_vs_L.SetMarkerColor(ROOT.kRed)
 
 mg = ROOT.TMultiGraph()
-mg.Add(dx_vs_ip)
+mg.Add(dx_vs_L)
 
 mg.Draw('AP')
 

### 2014-12-12 python/variable_eta.py

@@ -7,20 +7,20 @@ import sys
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_ip = ROOT.TGraph()
-ms_vs_ip = ROOT.TGraph()
+dx_vs_eta = ROOT.TGraph()
+ms_vs_eta = ROOT.TGraph()
 i = 0
-for m,n in zip(ms,ip):
-    dx_vs_ip.SetPoint(i,n,tr[0]+pr[0]-m)
-    ms_vs_ip.SetPoint(i,n,m)
+for m,n in zip(ms,eta):
+    dx_vs_eta.SetPoint(i,n,tr[0]+pr[0]-m)
+    ms_vs_eta.SetPoint(i,n,m)
     i = i + 1
 
-dx_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerColor(ROOT.kRed)
+dx_vs_eta.SetMarkerStyle(7)
+ms_vs_eta.SetMarkerStyle(7)
+ms_vs_eta.SetMarkerColor(ROOT.kRed)
 
 mg = ROOT.TMultiGraph()
-mg.Add(dx_vs_ip)
+mg.Add(dx_vs_eta)
 
 mg.Draw('AP')
 

### 2014-12-12 python/variable_pvinit.py

@@ -7,20 +7,20 @@ import sys
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_ip = ROOT.TGraph()
-ms_vs_ip = ROOT.TGraph()
+dx_vs_pvx0 = ROOT.TGraph()
+ms_vs_pvx0 = ROOT.TGraph()
 i = 0
-for m,n in zip(ms,ip):
-    dx_vs_ip.SetPoint(i,n,tr[0]+pr[0]-m)
-    ms_vs_ip.SetPoint(i,n,m)
+for m,n in zip(ms,pvx0):
+    dx_vs_pvx0.SetPoint(i,n,tr[0]+pr[0]-m)
+    ms_vs_pvx0.SetPoint(i,n,m)
     i = i + 1
 
-dx_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerColor(ROOT.kRed)
+dx_vs_pvx0.SetMarkerStyle(7)
+ms_vs_pvx0.SetMarkerStyle(7)
+ms_vs_pvx0.SetMarkerColor(ROOT.kRed)
 
 mg = ROOT.TMultiGraph()
-mg.Add(dx_vs_ip)
+mg.Add(dx_vs_pvx0)
 
 mg.Draw('AP')
 

### 2014-12-12 python/styleit.py
ya ya python plots 99 percent done

@@ -1,0 +1,54 @@
+import ROOT
+from ROOT import gStyle
+
+def gstyle():
+    ROOT.gROOT.ProcessLine('TGaxis::SetMaxDigits(3);')    
+    gStyle.SetFrameBorderMode(0)
+    gStyle.SetFrameFillColor(0)
+    gStyle.SetCanvasBorderMode(0)
+    gStyle.SetCanvasColor(0)
+    gStyle.SetPadBorderMode(0)
+    gStyle.SetPadColor(0)
+    gStyle.SetStatColor(0)
+    gStyle.SetTitleFont(42,'')
+    gStyle.SetLabelFont(42,'x')
+    gStyle.SetTitleFont(42,'x')
+    gStyle.SetLabelFont(42,'y')
+    gStyle.SetTitleFont(42,'y')
+    gStyle.SetLabelFont(42,'z')
+    gStyle.SetTitleFont(42,'z')
+    gStyle.SetLabelSize(0.042,'x')
+    gStyle.SetTitleSize(0.048,'x')
+    gStyle.SetLabelSize(0.042,'y')
+    gStyle.SetTitleSize(0.048,'y')
+    gStyle.SetLabelSize(0.042,'z')
+    gStyle.SetTitleSize(0.048,'z')
+    gStyle.SetTitleSize(0.048,'')
+    gStyle.SetTitleAlign(23)
+    gStyle.SetTitleX(0.5)
+    gStyle.SetTitleBorderSize(0)
+    gStyle.SetTitleFillColor(0)
+    gStyle.SetTitleStyle(0)
+    gStyle.SetOptStat(0)
+    gStyle.SetStatBorderSize(0)
+    gStyle.SetStatFont(42)
+    gStyle.SetStatFontSize(0.042)
+    gStyle.SetStatY(0.9)
+    gStyle.SetStatX(0.86)
+    gStyle.SetLegendBorderSize(0)
+    gStyle.SetLegendFillColor(0)
+    gStyle.SetFuncWidth(2)
+    gStyle.SetFuncColor(2)
+    gStyle.SetPadTopMargin(0.08)
+    gStyle.SetPadBottomMargin(0.12)
+    gStyle.SetPadLeftMargin(0.12)
+    gStyle.SetPadRightMargin(0.08)  
+    gStyle.SetCanvasDefX(400)
+    gStyle.SetCanvasDefY(20)
+    gStyle.SetCanvasDefH(420)
[…]

### 2014-12-12 python/variable_L.py

@@ -3,25 +3,44 @@
 import ROOT
 import numpy as np
 import sys
+from styleit import gstyle
+
+gstyle()
 
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_L = ROOT.TGraph()
-ms_vs_L = ROOT.TGraph()
+dx_vs_L  = ROOT.TGraph()
+vfp_vs_L = ROOT.TGraph()
+vft_vs_L = ROOT.TGraph()
+el_vs_L  = ROOT.TGraph()
+
+dx_vs_L.SetTitle(';#lambda;#Delta x_{max}')
+vfp_vs_L.SetTitle(';#lambda;Projectile v_{f}')
+vft_vs_L.SetTitle(';#lambda;Target v_{f}')
+el_vs_L.SetTitle(';#lambda;Energy Loss')
+
 i = 0
-for m,n in zip(ms,L):
-    dx_vs_L.SetPoint(i,n,tr[0]+pr[0]-m)
-    ms_vs_L.SetPoint(i,n,m)
+for iL, ipvx0, ims, ifvt, ifvp in zip(L,pvx0,ms,fvt,fvp):
+    dx_vs_L.SetPoint(i,iL,tr[0]+pr[0]-ims)
+    vfp_vs_L.SetPoint(i,iL,ifvp)
+    vft_vs_L.SetPoint(i,iL,ifvt)
+    el_vs_L.SetPoint(i,iL,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
     i = i + 1
-
+                     
 dx_vs_L.SetMarkerStyle(7)
-ms_vs_L.SetMarkerStyle(7)
-ms_vs_L.SetMarkerColor(ROOT.kRed)
+el_vs_L.SetMarkerStyle(7)
+vft_vs_L.SetMarkerStyle(7)
+vft_vs_L.SetMarkerColor(ROOT.kBlue)
+vfp_vs_L.SetMarkerStyle(7)
+vfp_vs_L.SetMarkerColor(ROOT.kRed)
 
-mg = ROOT.TMultiGraph()
-mg.Add(dx_vs_L)
-
[…]

### 2014-12-12 python/variable_eta.py

@@ -3,25 +3,44 @@
 import ROOT
 import numpy as np
 import sys
+from styleit import gstyle
+
+gstyle()
 
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_eta = ROOT.TGraph()
-ms_vs_eta = ROOT.TGraph()
+dx_vs_eta  = ROOT.TGraph()
+vfp_vs_eta = ROOT.TGraph()
+vft_vs_eta = ROOT.TGraph()
+el_vs_eta  = ROOT.TGraph()
+
+dx_vs_eta.SetTitle(';#eta;#Delta x_{max}')
+vfp_vs_eta.SetTitle(';#eta;Projectile v_{f}')
+vft_vs_eta.SetTitle(';#eta;Target v_{f}')
+el_vs_eta.SetTitle(';#eta;Energy Loss')
+
 i = 0
-for m,n in zip(ms,eta):
-    dx_vs_eta.SetPoint(i,n,tr[0]+pr[0]-m)
-    ms_vs_eta.SetPoint(i,n,m)
+for ieta, ipvx0, ims, ifvt, ifvp in zip(eta,pvx0,ms,fvt,fvp):
+    dx_vs_eta.SetPoint(i,ieta,tr[0]+pr[0]-ims)
+    vfp_vs_eta.SetPoint(i,ieta,ifvp)
+    vft_vs_eta.SetPoint(i,ieta,ifvt)
+    el_vs_eta.SetPoint(i,ieta,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
     i = i + 1
-
+                     
 dx_vs_eta.SetMarkerStyle(7)
-ms_vs_eta.SetMarkerStyle(7)
-ms_vs_eta.SetMarkerColor(ROOT.kRed)
+el_vs_eta.SetMarkerStyle(7)
+vft_vs_eta.SetMarkerStyle(7)
+vft_vs_eta.SetMarkerColor(ROOT.kBlue)
+vfp_vs_eta.SetMarkerStyle(7)
+vfp_vs_eta.SetMarkerColor(ROOT.kRed)
 
[…]

### 2014-12-12 python/variable_pvinit.py

@@ -3,25 +3,44 @@
 import ROOT
 import numpy as np
 import sys
+from styleit import gstyle
+
+gstyle()
 
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_pvx0 = ROOT.TGraph()
-ms_vs_pvx0 = ROOT.TGraph()
+dx_vs_pvinit  = ROOT.TGraph()
+vfp_vs_pvinit = ROOT.TGraph()
+vft_vs_pvinit = ROOT.TGraph()
+el_vs_pvinit  = ROOT.TGraph()
+
+dx_vs_pvinit.SetTitle(';Projectile v_{0};#Delta x_{max}')
+vfp_vs_pvinit.SetTitle(';Projectile v_{0};Projectile v_{f}')
+vft_vs_pvinit.SetTitle(';Projectile v_{0};Target v_{f}')
+el_vs_pvinit.SetTitle(';Projectile v_{0};Energy Loss')
+
 i = 0
-for m,n in zip(ms,pvx0):
-    dx_vs_pvx0.SetPoint(i,n,tr[0]+pr[0]-m)
-    ms_vs_pvx0.SetPoint(i,n,m)
+for ipvinit, ipvx0, ims, ifvt, ifvp in zip(pvx0,pvx0,ms,fvt,fvp):
+    dx_vs_pvinit.SetPoint(i,ipvinit,tr[0]+pr[0]-ims)
+    vfp_vs_pvinit.SetPoint(i,ipvinit,ifvp)
+    vft_vs_pvinit.SetPoint(i,ipvinit,ifvt)
+    el_vs_pvinit.SetPoint(i,ipvinit,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
     i = i + 1
+                     
+dx_vs_pvinit.SetMarkerStyle(7)
+el_vs_pvinit.SetMarkerStyle(7)
+vft_vs_pvinit.SetMarkerStyle(7)
+vft_vs_pvinit.SetMarkerColor(ROOT.kBlue)
+vfp_vs_pvinit.SetMarkerStyle(7)
[…]

### 2014-12-12 python/variable_s.py

@@ -3,25 +3,44 @@
 import ROOT
 import numpy as np
 import sys
+from styleit import gstyle
+
+gstyle()
 
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
 
-dx_vs_ip = ROOT.TGraph()
-ms_vs_ip = ROOT.TGraph()
+dx_vs_ip  = ROOT.TGraph()
+vfp_vs_ip = ROOT.TGraph()
+vft_vs_ip = ROOT.TGraph()
+el_vs_ip  = ROOT.TGraph()
+
+dx_vs_ip.SetTitle(';s;#Delta x_{max}')
+vfp_vs_ip.SetTitle(';s;Projectile v_{f}')
+vft_vs_ip.SetTitle(';s;Target v_{f}')
+el_vs_ip.SetTitle(';s;Energy Loss')
+
 i = 0
-for m,n in zip(ms,ip):
-    dx_vs_ip.SetPoint(i,n,tr[0]+pr[0]-m)
-    ms_vs_ip.SetPoint(i,n,m)
+for iip, ipvx0, ims, ifvt, ifvp in zip(ip,pvx0,ms,fvt,fvp):
+    dx_vs_ip.SetPoint(i,iip,tr[0]+pr[0]-ims)
+    vfp_vs_ip.SetPoint(i,iip,ifvp)
+    vft_vs_ip.SetPoint(i,iip,ifvt)
+    el_vs_ip.SetPoint(i,iip,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
     i = i + 1
-
+                     
 dx_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerStyle(7)
-ms_vs_ip.SetMarkerColor(ROOT.kRed)
+el_vs_ip.SetMarkerStyle(7)
+vft_vs_ip.SetMarkerStyle(7)
+vft_vs_ip.SetMarkerColor(ROOT.kBlue)
+vfp_vs_ip.SetMarkerStyle(7)
+vfp_vs_ip.SetMarkerColor(ROOT.kRed)
 
-mg = ROOT.TMultiGraph()
[…]

### 2014-12-12 main.cpp
giving more room on object plots

@@ -331,9 +331,9 @@ int main(int argc, char *argv[])
 
   
   c2we->Modified(); c2we->Update();
-  mgxy->GetXaxis()->SetLimits(-2.2*target_radius,2.2*target_radius);
+  mgxy->GetXaxis()->SetLimits(-3*target_radius,3*target_radius);
   c2we->Modified(); c2we->Update();
-  mgxy->GetYaxis()->SetRangeUser(-2.2*target_radius,2.2*target_radius);
+  mgxy->GetYaxis()->SetRangeUser(-3*target_radius,3*target_radius);
   gPad->Modified();
   c2we->Print("out/x_vs_y_with_ellipse.pdf", "Portrait pdf");
   
@@ -345,9 +345,9 @@ int main(int argc, char *argv[])
 
   
   c2weMS->Modified(); c2weMS->Update();
-  mgxy->GetXaxis()->SetLimits(-2.2*target_radius,2.2*target_radius);
+  mgxy->GetXaxis()->SetLimits(-3*target_radius,3*target_radius);
   c2weMS->Modified(); c2weMS->Update();
-  mgxy->GetYaxis()->SetRangeUser(-2.2*target_radius,2.2*target_radius);
+  mgxy->GetYaxis()->SetRangeUser(-3*target_radius,3*target_radius);
   gPad->Modified();
   c2weMS->Print("out/x_vs_y_with_ellipse_MS.pdf", "Portrait pdf");
 

### 2014-12-12 paper/formatting.tex
paper up

\definecolor{mykeyword}{rgb}{139, 0, 139}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{blue},       % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=none,                      % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{mykeyword},  % keyword style
  language=c++,                    % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{red},         % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

### 2014-12-12 paper/paper.tex
paper up

@@
 \usepackage{graphicx}
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage{indentfirst}
+\usepackage{listings}
+\usepackage{color}
+\usepackage[title,titletoc,toc]{appendix}
+\usepackage[hidelinks,hyperfootnotes=false,bookmarks=false]{hyperref}
 \usepackage{epsfig}
+\usepackage{setspace}
+
+\setlength{\paperheight}{11in}
+
+\input{formatting}
+
 \begin{document}
 \title{Modeling Two Body Collisions with Spring Potential Interactions}
-\author{Matthew Epland, Douglas Davis}
+\author{Matthew \textsc{Epland}, Douglas \textsc{Davis}}
 \affiliation{Department of Physics, Duke University}
 \date{\today}
+
+\hypersetup{pdftitle=Modeling Two Body Collisions}
+\hypersetup{pdfauthor={Matthew Epland, Douglas Davis}}
+%\hypersetup{bookmarks=false}
+\hypersetup{pdfkeywords={Classical Physics, Two Body Collisions}}
+
 \begin{abstract}
-  This report describes a computational study of two body collisions where the dynamics of the bodies are governed by a Hooke's Law type force at the interaction points.
-We investigate a number of scenarios which involve a stationary target object which is contacted by a projectile object with some horizontal velocity in a two dimensional plane.
-Object trajectories are determined from a simulation software package, along with other various kinematic variables.
-Parameters governing the interactions and the kinematics are changed to study various trends in the kinematic variables for different scenarios.
+This paper describes a computational study of two body collisions where the dynamics of the bodies are governed by a Hooke's Law type force at the interaction points.
+We investigate a number of scenarios which involve both a stationary target mass which is stuck by a projectile mass with some horizontal velocity in a two dimensional plane, as well as scenarios where both masses are moving in towards each other.
+The masses trajectories are determined from a simulation software package, written by the authors, that models the force between the masses as they interact with each other based on the initial kinematic state of the system.
+Specific attention was given to the systems behavior with different initial projectile velocities, impact parameters, energy loss rates and power dependence in the force law.
 \end{abstract}\maketitle
-\section{yar}
-this is cool.
+\section{Introduction}
+When two classical objects physically collide they experience a normal force between them.
+In the simplest case, that of two spherical masses, the normal force is orthogonal to the surface and is in line with the center of mass for both the objects.
+The magnitude of the normal force between masses $m_{1}$, $m_{2}$ with radii $r_{1}$, $r_{2}$ can be modeled as $ \left| F \right| = k \left(\Delta x\right)^{\lambda}$, where $\Delta x = r_1 + r_2 - \left| \mathbf{x}^{(1)}-\mathbf{x}^{(2)} \right|$ is the displacement from equilibrium and $k$ is an effective spring constant.
+Setting $\lambda = 1$ results in the familiar Hook's Law spring force, but by including the $\lambda$ power dependence we are able to study a wider array of collisions, particularly those where the masses deform enough that the normal force between them becomes nonlinear.
+As the masses deform and push against each other some of the mechanical energy of the system may be lost to internal degrees of freedom, such as heat.
+One way to model these inelastic collisions is by including viscous damping proportional to the velocity, which was the method used in this study.
+
+Any two body collision can be reduced to 2-dimensional motion in a plane containing both masses and their initial velocity vectors.
+Additionally, in this paper we limit ourselves to the case where the initial velocities are parallel, though the masses may be initially off center from each other by a distance $s$, the impact parameter.
+One of the masses, the target $m_{1}$, may be at rest initially, though we also allow it to have an initial closing velocity in some studies.
+For continence we pick our coordinate system such that all the initial velocities lie along $\hat{x}$ and the target is on the $\hat{y}$ axis, $y_{1}(t=0)=0$ (Figure~\ref{fig:schematic}).
+
+\begin{figure}[htbc]
+	\centering
+	\includegraphics[width=.75\textwidth]{plots/cj_diag.pdf}
+	{\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+	\caption{Schematic View of the initial state at first contact, $t = 0$.}
+	\label{fig:schematic}
+\end{figure}
+
+In order to rapidly investigate the many possible variations of this seemingly simple two body collision a software simulation was chosen over attempting to solve each variation analytically.
+Written in C++ and using some of the ROOT particle physics analysis libraries the simulation code at its core operates by iteratively calculating the masses change in position and velocity during a small time step, $\Delta t$, during which the acceleration is assumed to be constant.
+This is done by calculating $\Delta x$ \eqref{eq:displacement} from the $n-1$ positions, and then $\left|F\right|$ and the unit vector between the two masses centers $\hat{F}_{j\text{ on }i}$ \eqref{eq:force}.
+Once the force has been estimated it is a simple matter to compute the $n$ time step positions \eqref{eq:position}, and velocities \eqref{eq:velocity}.
+When calculating the velocity we include a $\left(1-\eta\right)$ term to implement the viscous dampening energy losses were $\eta$ is the proportional decrease in velocity per time step.
+
+\begin{equation}\label{eq:position}
+\mathbf{x}^{(i)}_{n} = \mathbf{x}^{(i)}_{n-1} + \dot{\mathbf{x}}^{(i)}_{n-1} \Delta t + \frac{1}{2m_i} \left| F \right| \mathbf{\hat{F}}_{j\text{ on }i} \left(\Delta t\right)^2
+\end{equation}
+\begin{equation}\label{eq:velocity}
+\dot{\mathbf{x}}^{(i)}_{n} = (1-\eta)\dot{\mathbf{x}}^{(i)}_{n-1} + \frac{1}{m_i} \left| F \right| \mathbf{\hat{F}}_{j\text{ on }i} \Delta t
+\end{equation}
+\begin{equation}\label{eq:displacement}
+\Delta x_{n-1} = r_1 + r_2 - \left| \mathbf{x}^{(1)}_{n-1}-\mathbf{x}^{(2)}_{n-1} \right|
+\end{equation}
+\begin{equation}\label{eq:force}
+\left| F \right| = k \left(\Delta x_{n-1}\right)^{\lambda},\quad \mathbf{\hat{F}}_{j\text{ on }i} = \frac{\mathbf{x}^{(i)}_{n-1}-\mathbf{x}^{(j)}_{n-1}}{\left|\mathbf{x}^{(i)}_{n-1}-\mathbf{x}^{(j)}_{n-1}\right|}
+\end{equation}
+
+In addition to the position and velocity of the masses we also calculate their kinetic energies and the potential energy stored in the deformed bodies, e.g.
+spring \eqref{eq:energy}.
+The force is conservative, so $\mathbf{F} = - \nabla V \rightarrow V = \int \left|F\right| dx$.
+With a small enough $\Delta t$ these iterative equations model the physics of the interaction very well.
+\begin{equation}\label{eq:energy}
+V_n = \frac{k}{\lambda+1}\left(\Delta x_n\right)^{\lambda+1},\quad T_n = \frac{m_1}{2}\left(\dot{\mathbf{x}}^{(1)}_n\right)^2 + \frac{m_2}{2}\left(\dot{\mathbf{x}}^{(2)}_n\right)^2
+\end{equation}
+
+\section{Results}
+\subsection{Simulation Performance}
+The simulation was good, here's why - include the single event plots
+
+\subsection{Initial Velocity Studies}
+The
+
+\subsection{Impact Parameter Studies}
+The
+
+\subsection{Force Power Law Dependence}
+The
+
+\subsection{Energy Dissipation Studies}
+The
+
+\section{Conclusion}
+The
+
+\clearpage
+\begin{appendices}
+\singlespacing
+\section{main.cpp} \label{sec:main}
+%\lstinputlisting{main.cpp}% lots of pages, only uncomment when you want it
+% use [firstline=, lastline=] to select only the physics loop
+
+\end{appendices}
+
 \end{document}

### 2014-12-12 main.cpp
changed default to have equal density objects

@@ -57,9 +57,9 @@ int main(int argc, char *argv[])
   desc.add_options()
     ("help,h","Print help message")
     ("p-radius", po::value<double>()->default_value(1.000),"projectile radius")
-    ("t-radius", po::value<double>()->default_value(3.000),"target radius")
-    ("p-mass",   po::value<double>()->default_value(1.000),"projectile mass")
-    ("t-mass",   po::value<double>()->default_value(5.000),"target mass")
+    ("t-radius", po::value<double>()->default_value(2.000),"target radius")
+    ("p-mass",   po::value<double>()->default_value(0.250),"projectile mass")
+    ("t-mass",   po::value<double>()->default_value(2.000),"target mass")
     ("p-vinit",  po::value<double>()->default_value(5.000),"projectile initial velocity")
     ("t-vinit",  po::value<double>()->default_value(0.000),"target initial velocity")
     ("delta-t,t",po::value<double>()->default_value(0.001),"time step")

### 2014-12-12 main.cpp
ok fixed default again needed change in impact param

@@ -63,7 +63,7 @@ int main(int argc, char *argv[])
     ("p-vinit",  po::value<double>()->default_value(5.000),"projectile initial velocity")
     ("t-vinit",  po::value<double>()->default_value(0.000),"target initial velocity")
     ("delta-t,t",po::value<double>()->default_value(0.001),"time step")
-    ("impact,s", po::value<double>()->default_value(2.000),"impact parameter")
+    ("impact,s", po::value<double>()->default_value(1.000),"impact parameter")
     ("spring,k", po::value<double>()->default_value(100.0),"spring constant")
     ("eta,e",    po::value<double>()->default_value(0.000),"energy disipation")
     ("lambda,l", po::value<double>()->default_value(1.000),"power law")

### 2014-12-12 paper/paper.tex
starting to put default system into the paper

@@
 In order to rapidly investigate the many possible variations of this seemingly simple two body collision a software simulation was chosen over attempting to solve each variation analytically.
-Written in C++ and using some of the ROOT particle physics analysis libraries the simulation code at its core operates by iteratively calculating the masses change in position and velocity during a small time step, $\Delta t$, during which the acceleration is assumed to be constant.
+Written in C++ and using some of the \texttt{ROOT}~\cite{ref_root} particle physics analysis libraries the simulation code at its core operates by iteratively calculating the masses change in position and velocity during a small time step, $\Delta t$, during which the acceleration is assumed to be constant.
 This is done by calculating $\Delta x$ \eqref{eq:displacement} from the $n-1$ positions, and then $\left|F\right|$ and the unit vector between the two masses centers $\hat{F}_{j\text{ on }i}$ \eqref{eq:force}.
@@
 \subsection{Simulation Performance}
-The simulation was good, here's why - include the single event plots
+One of the first tasks was to validate the simulation framework using a system where the physics was simple and easy to intuitively predict.
+This system uses a stationary target of radius units 2, with a projectile of radius units 1 incoming at velocity units 5 with an impact parameter of 1 unit.
+The objects have equal density.
+We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ force constant.
+First we visualize the track points for each objects tracjectory while they are in contact with each other.
+\begin{figure}[h!]
+  \includegraphics[width=.45\textwidth]{../diff_system_plots/default/x_vs_y_with_ellipse.pdf}
+  \includegraphics[width=.45\textwidth]{../diff_system_plots/default/x_vs_y_with_ellipse_MS.pdf}
+  	          {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+  \caption{(L) The initial state of the system when the objects come in contact.
+The collections of points (which form a continuous line) show the position of the center of each object at each time step while the objects are in contact.
+(R) The state of the system when the objects are at a minimum separation (maximum $\Delta x$ from equilibrium).}
+  \label{fig:tracks_default}
+\end{figure}
 
@@
 
+\begin{thebibliography}{9}
+\bibitem{ref_root}
+  R.~Brun and F.~Rademakers, \emph{ROOT - An Object Oriented Data Analysis Framework}, Proceedings AIHENP 96 Workshop, Lausanne, Sep.
+1996, Nucl.
+Inst.
+\& Meth.
+in Phys.
+Res.
+A 389 (1997) 81-86.
+See also http://root.cern.ch/.
+
+\end{thebibliography}
 \end{document}

### 2014-12-12 paper/paper.tex
ignore updated

@@
 In order to rapidly investigate the many possible variations of this seemingly simple two body collision a software simulation was chosen over attempting to solve each variation analytically.
-Written in C++ and using some of the \texttt{ROOT}~\cite{ref_root} particle physics analysis libraries the simulation code at its core operates by iteratively calculating the masses change in position and velocity during a small time step, $\Delta t$, during which the acceleration is assumed to be constant.
+Written in \texttt{C++} and using some of the \texttt{ROOT}~\cite{ref_root} particle physics analysis libraries the simulation code at its core operates by iteratively calculating the object's change in position and velocity during a small time step, $\Delta t$, during which the acceleration is assumed to be constant.
 This is done by calculating $\Delta x$ \eqref{eq:displacement} from the $n-1$ positions, and then $\left|F\right|$ and the unit vector between the two masses centers $\hat{F}_{j\text{ on }i}$ \eqref{eq:force}.

### 2014-12-12 paper/paper.tex
paper update

@@
 First we visualize the track points for each objects tracjectory while they are in contact with each other.
+We show this visualization in Figure~\ref{fig:tracks_default}.
 \begin{figure}[h!]
@@
                   \label{fig:tracks_default}
+\end{figure}
+We also check for kinematic trends to be physically sound for the given initial conditions and parameters of the system.
+\begin{figure}
+  \includegraphics[width=.8\textwidth]{../diff_system_plots/default/E_vs_t.pdf}
+  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+  \caption{Trends for different energies in the system: object and total kinetic energies, potential energy, and the total energy of the system.}
 \end{figure}

### 2014-12-12 python/variable_eta.py
python plots

@@ -15,17 +15,17 @@ vfp_vs_eta = ROOT.TGraph()
 vft_vs_eta = ROOT.TGraph()
 el_vs_eta  = ROOT.TGraph()
 
-dx_vs_eta.SetTitle(';#eta;#Delta x_{max}')
+dx_vs_eta.SetTitle(';#eta;#Delta x_{max}/r_{t}')
 vfp_vs_eta.SetTitle(';#eta;Projectile v_{f}')
 vft_vs_eta.SetTitle(';#eta;Target v_{f}')
-el_vs_eta.SetTitle(';#eta;Energy Loss')
+el_vs_eta.SetTitle(';#eta;(E_{0}-E_{f})/E_{0}')
 
 i = 0
 for ieta, ipvx0, ims, ifvt, ifvp in zip(eta,pvx0,ms,fvt,fvp):
-    dx_vs_eta.SetPoint(i,ieta,tr[0]+pr[0]-ims)
+    dx_vs_eta.SetPoint(i,ieta,(tr[0]+pr[0]-ims)/tr[0])
     vfp_vs_eta.SetPoint(i,ieta,ifvp)
     vft_vs_eta.SetPoint(i,ieta,ifvt)
-    el_vs_eta.SetPoint(i,ieta,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
+    el_vs_eta.SetPoint(i,ieta,(0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))/(0.5*pm[0]*ipvx0*ipvx0))
     i = i + 1
                      
 dx_vs_eta.SetMarkerStyle(7)

### 2014-12-12 python/variable_pvinit.py

@@ -15,17 +15,17 @@ vfp_vs_pvinit = ROOT.TGraph()
 vft_vs_pvinit = ROOT.TGraph()
 el_vs_pvinit  = ROOT.TGraph()
 
-dx_vs_pvinit.SetTitle(';Projectile v_{0};#Delta x_{max}')
+dx_vs_pvinit.SetTitle(';Projectile v_{0};#frac{#Delta x_{max}}{r_{t}}')
 vfp_vs_pvinit.SetTitle(';Projectile v_{0};Projectile v_{f}')
 vft_vs_pvinit.SetTitle(';Projectile v_{0};Target v_{f}')
-el_vs_pvinit.SetTitle(';Projectile v_{0};Energy Loss')
+el_vs_pvinit.SetTitle(';Projectile v_{0};(E_{0}-E_{f})/E_{0}')
 
 i = 0
 for ipvinit, ipvx0, ims, ifvt, ifvp in zip(pvx0,pvx0,ms,fvt,fvp):
-    dx_vs_pvinit.SetPoint(i,ipvinit,tr[0]+pr[0]-ims)
+    dx_vs_pvinit.SetPoint(i,ipvinit,(tr[0]+pr[0]-ims)/tr[0])
     vfp_vs_pvinit.SetPoint(i,ipvinit,ifvp)
     vft_vs_pvinit.SetPoint(i,ipvinit,ifvt)
-    el_vs_pvinit.SetPoint(i,ipvinit,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
+    el_vs_pvinit.SetPoint(i,ipvinit,(0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))/(0.5*pm[0]*ipvx0*ipvx0))
     i = i + 1
                      
 dx_vs_pvinit.SetMarkerStyle(7)
@@ -36,6 +36,7 @@ vfp_vs_pvinit.SetMarkerStyle(7)
 vfp_vs_pvinit.SetMarkerColor(ROOT.kRed)
 
 c1 = ROOT.TCanvas()
+dx_vs_pvinit.GetYaxis().SetTitleOffset(.89)
 dx_vs_pvinit.Draw('AP')
 c2 = ROOT.TCanvas()
 el_vs_pvinit.Draw('AP')

### 2014-12-12 paper/paper.tex
moved plots, edited paper, finalized main.cpp

@@
 Written in \texttt{C++} and using some of the \texttt{ROOT}~\cite{ref_root} particle physics analysis libraries the simulation code at its core operates by iteratively calculating the object's change in position and velocity during a small time step, $\Delta t$, during which the acceleration is assumed to be constant.
-This is done by calculating $\Delta x$ \eqref{eq:displacement} from the $n-1$ positions, and then $\left|F\right|$ and the unit vector between the two masses centers $\hat{F}_{j\text{ on }i}$ \eqref{eq:force}.
+This is done by calculating $\Delta x$ \eqref{eq:displacement} from the $n-1$ positions, and then $\left|F\right|$ and the unit vector between the two masses centers $\mathbf{\hat{F}}_{j\rightarrow i}$ \eqref{eq:force}.
 Once the force has been estimated it is a simple matter to compute the $n$ time step positions \eqref{eq:position}, and velocities \eqref{eq:velocity}.
@@
 \begin{equation}\label{eq:position}
-  \mathbf{x}^{(i)}_{n} = \mathbf{x}^{(i)}_{n-1} + \dot{\mathbf{x}}^{(i)}_{n-1} \Delta t + \frac{1}{2m_i} \left| F \right| \mathbf{\hat{F}}_{j\text{ on }i} \left(\Delta t\right)^2
+  \mathbf{x}^{(i)}_{n} = \mathbf{x}^{(i)}_{n-1} + \dot{\mathbf{x}}^{(i)}_{n-1} \Delta t + \frac{1}{2m_i} \left| F \right| \mathbf{\hat{F}}_{j\rightarrow i} \left(\Delta t\right)^2
 \end{equation}
+
 \begin{equation}\label{eq:velocity}
-  \dot{\mathbf{x}}^{(i)}_{n} = (1-\eta)\dot{\mathbf{x}}^{(i)}_{n-1} + \frac{1}{m_i} \left| F \right| \mathbf{\hat{F}}_{j\text{ on }i} \Delta t
+  \dot{\mathbf{x}}^{(i)}_{n} = (1-\eta)\dot{\mathbf{x}}^{(i)}_{n-1} + \frac{1}{m_i} \left| F \right| \mathbf{\hat{F}}_{j\rightarrow i} \Delta t
 \end{equation}
@@
 \begin{equation}\label{eq:force}
-  \left| F \right| = k \left(\Delta x_{n-1}\right)^{\lambda},\quad \mathbf{\hat{F}}_{j\text{ on }i} = \frac{\mathbf{x}^{(i)}_{n-1}-\mathbf{x}^{(j)}_{n-1}}{\left|\mathbf{x}^{(i)}_{n-1}-\mathbf{x}^{(j)}_{n-1}\right|}
+  \left| F \right| = k \left(\Delta x_{n-1}\right)^{\lambda},\quad \mathbf{\hat{F}}_{j\rightarrow i} = \frac{\mathbf{x}^{(i)}_{n-1}-\mathbf{x}^{(j)}_{n-1}}{\left|\mathbf{x}^{(i)}_{n-1}-\mathbf{x}^{(j)}_{n-1}\right|}
 \end{equation}
@@
 spring \eqref{eq:energy}.
-The force is conservative, so $\mathbf{F} = - \nabla V \rightarrow V = \int \left|F\right| dx$.
+The force is conservative, so $\mathbf{F} = - \nabla V \rightarrow V = \int \left|F\right| d\left(\Delta x\right)$.
 With a small enough $\Delta t$ these iterative equations model the physics of the interaction very well.
+To ensure that $\Delta t$ is not set too large the code checks each masses change in position at every time step.
+If the change in position is larger than 1\% of the masses radius a warning is generated and the simulation is re-run with a smaller $\Delta t$
 \begin{equation}\label{eq:energy}
@@
 \clearpage
-\begin{appendices}
-  \singlespacing
-  \section{main.cpp} \label{sec:main}
-  %\lstinputlisting{main.cpp}% lots of pages, only uncomment when you want it
-  % use [firstline=, lastline=] to select only the physics loop
-
-\end{appendices}
-
 \begin{thebibliography}{9}
+\section{Bibliography}
 \bibitem{ref_root}
@@
 \end{thebibliography}
+
+\clearpage
+\begin{appendices}
+  \singlespacing
+  \section{main.cpp Physics Loop} \label{sec:main.cpp}
+  \lstinputlisting[firstline=170, lastline=246]{../main.cpp}% lots of pages, only uncomment when you want it
+
+\end{appendices}
+
 \end{document}

### 2014-12-12 main.cpp

@@ -274,7 +274,8 @@ int main(int argc, char *argv[])
   
   TGraph *sep_graph = new TGraph(sep_vector.size(),&time_vector[0],&sep_vector[0]);
   sep_graph->GetXaxis()->SetTitle("t");
-  sep_graph->GetYaxis()->SetTitle("#||{#vec{x_{1}}-#vec{x_{2}}}");
+  sep_graph->GetYaxis()->SetTitle("#||{#vec{x^{(1)}}-#vec{x^{(2)}}}");
+  sep_graph->GetYaxis()->SetTitleOffset(1.6);
   sep_graph->SetMarkerStyle(7);
   sep_graph->Draw("AP");
   sep_graph->SetTitle("Radial Seperation vs Time");
@@ -312,7 +313,7 @@ int main(int argc, char *argv[])
   mgxy->SetTitle("Center of Mass Trajectories");
   mgxy->GetXaxis()->SetTitle("x");
   mgxy->GetYaxis()->SetTitle("y");
-  mgxy->GetYaxis()->SetTitleOffset(1.25); // This plot looked bad it without it but not the others for some reason... ?
+  mgxy->GetYaxis()->SetTitleOffset(1.25);
 
   TLegend* mgxyleg = new TLegend(0.15,0.75,0.4,0.9);
   mgxyleg->AddEntry(xy2,"Projectile","p");
@@ -487,6 +488,7 @@ int main(int argc, char *argv[])
   TGraph *Fmag_graph = new TGraph(Fmag_vector.size(),&time_vector[0],&Fmag_vector[0]);
   Fmag_graph->GetXaxis()->SetTitle("t");
   Fmag_graph->GetYaxis()->SetTitle("#||{F}");
+  Fmag_graph->GetYaxis()->SetTitleOffset(1.45);
   Fmag_graph->SetMarkerStyle(7);
   Fmag_graph->Draw("AP");
   Fmag_graph->SetTitle("Force Magnitude vs Time");

### 2014-12-12 paper/paper.tex
working paths in paper

@@
 \begin{figure}[h!]
-  \includegraphics[width=.45\textwidth]{../diff_system_plots/default/x_vs_y_with_ellipse.pdf}
-  \includegraphics[width=.45\textwidth]{../diff_system_plots/default/x_vs_y_with_ellipse_MS.pdf}
+  \includegraphics[width=.45\textwidth]{plots/default/x_vs_y_with_ellipse.pdf}
+  \includegraphics[width=.45\textwidth]{plots/default/x_vs_y_with_ellipse_MS.pdf}
                   {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
@@
 \begin{figure}
-  \includegraphics[width=.8\textwidth]{../diff_system_plots/default/E_vs_t.pdf}
+  \includegraphics[width=.8\textwidth]{plots/default/E_vs_t.pdf}
   {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}

### 2014-12-12 python/variable_L.py
python plots ya

@@ -15,14 +15,14 @@ vfp_vs_L = ROOT.TGraph()
 vft_vs_L = ROOT.TGraph()
 el_vs_L  = ROOT.TGraph()
 
-dx_vs_L.SetTitle(';#lambda;#Delta x_{max}')
+dx_vs_L.SetTitle(';#lambda;#frac{#Delta x_{max}}{r_{t}}')
 vfp_vs_L.SetTitle(';#lambda;Projectile v_{f}')
 vft_vs_L.SetTitle(';#lambda;Target v_{f}')
 el_vs_L.SetTitle(';#lambda;Energy Loss')
 
 i = 0
 for iL, ipvx0, ims, ifvt, ifvp in zip(L,pvx0,ms,fvt,fvp):
-    dx_vs_L.SetPoint(i,iL,tr[0]+pr[0]-ims)
+    dx_vs_L.SetPoint(i,iL,(tr[0]+pr[0]-ims)/tr[0])
     vfp_vs_L.SetPoint(i,iL,ifvp)
     vft_vs_L.SetPoint(i,iL,ifvt)
     el_vs_L.SetPoint(i,iL,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
@@ -36,6 +36,7 @@ vfp_vs_L.SetMarkerStyle(7)
 vfp_vs_L.SetMarkerColor(ROOT.kRed)
 
 c1 = ROOT.TCanvas()
+dx_vs_L.GetYaxis().SetTitleOffset(.89)
 dx_vs_L.Draw('AP')
 c2 = ROOT.TCanvas()
 el_vs_L.Draw('AP')

### 2014-12-12 python/variable_eta.py

@@ -15,14 +15,14 @@ vfp_vs_eta = ROOT.TGraph()
 vft_vs_eta = ROOT.TGraph()
 el_vs_eta  = ROOT.TGraph()
 
-dx_vs_eta.SetTitle(';#eta;#Delta x_{max}/r_{t}')
+dx_vs_eta.SetTitle(';#eta;#frac{#Delta x_{max}}{r_{t}} #times 10')
 vfp_vs_eta.SetTitle(';#eta;Projectile v_{f}')
 vft_vs_eta.SetTitle(';#eta;Target v_{f}')
 el_vs_eta.SetTitle(';#eta;(E_{0}-E_{f})/E_{0}')
 
 i = 0
 for ieta, ipvx0, ims, ifvt, ifvp in zip(eta,pvx0,ms,fvt,fvp):
-    dx_vs_eta.SetPoint(i,ieta,(tr[0]+pr[0]-ims)/tr[0])
+    dx_vs_eta.SetPoint(i,ieta,10*(tr[0]+pr[0]-ims)/tr[0])
     vfp_vs_eta.SetPoint(i,ieta,ifvp)
     vft_vs_eta.SetPoint(i,ieta,ifvt)
     el_vs_eta.SetPoint(i,ieta,(0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))/(0.5*pm[0]*ipvx0*ipvx0))
@@ -36,6 +36,7 @@ vfp_vs_eta.SetMarkerStyle(7)
 vfp_vs_eta.SetMarkerColor(ROOT.kRed)
 
 c1 = ROOT.TCanvas()
+dx_vs_eta.GetYaxis().SetTitleOffset(.89)
 dx_vs_eta.Draw('AP')
 c2 = ROOT.TCanvas()
 el_vs_eta.Draw('AP')

### 2014-12-12 python/variable_pvinit.py

@@ -37,11 +37,15 @@ vfp_vs_pvinit.SetMarkerColor(ROOT.kRed)
 
 c1 = ROOT.TCanvas()
 dx_vs_pvinit.GetYaxis().SetTitleOffset(.89)
+dx_vs_pvinit.GetXaxis().SetTitleOffset(.95)
 dx_vs_pvinit.Draw('AP')
 c2 = ROOT.TCanvas()
+el_vs_pvinit.GetXaxis().SetTitleOffset(.95)
 el_vs_pvinit.Draw('AP')
 c3 = ROOT.TCanvas()
+vfp_vs_pvinit.GetXaxis().SetTitleOffset(.95)
 vfp_vs_pvinit.Draw('AP')
 c4 = ROOT.TCanvas()
+vft_vs_pvinit.GetXaxis().SetTitleOffset(.95)
 vft_vs_pvinit.Draw('AP')
 raw_input('')

### 2014-12-12 python/variable_s.py

@@ -5,6 +5,8 @@ import numpy as np
 import sys
 from styleit import gstyle
 
+ROOT.gROOT.ProcessLine("TGaxis::SetMaxDigits(2);")
+
 gstyle()
 
 data = np.loadtxt(sys.argv[1])
@@ -15,14 +17,16 @@ vfp_vs_ip = ROOT.TGraph()
 vft_vs_ip = ROOT.TGraph()
 el_vs_ip  = ROOT.TGraph()
 
-dx_vs_ip.SetTitle(';s;#Delta x_{max}')
+dx_vs_ip.SetTitle(';s;#frac{#Delta x_{max}}{r_{t}}')
 vfp_vs_ip.SetTitle(';s;Projectile v_{f}')
 vft_vs_ip.SetTitle(';s;Target v_{f}')
 el_vs_ip.SetTitle(';s;Energy Loss')
 
 i = 0
 for iip, ipvx0, ims, ifvt, ifvp in zip(ip,pvx0,ms,fvt,fvp):
-    dx_vs_ip.SetPoint(i,iip,tr[0]+pr[0]-ims)
+    if ifvp > 4.8:
+        continue
+    dx_vs_ip.SetPoint(i,iip,(tr[0]+pr[0]-ims)/tr[0])
     vfp_vs_ip.SetPoint(i,iip,ifvp)
     vft_vs_ip.SetPoint(i,iip,ifvt)
     el_vs_ip.SetPoint(i,iip,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))

### 2014-12-12 python/styleit.py
python plots done

@@ -2,7 +2,7 @@ import ROOT
 from ROOT import gStyle
 
 def gstyle():
-    ROOT.gROOT.ProcessLine('TGaxis::SetMaxDigits(3);')    
+    ROOT.gROOT.ProcessLine('TGaxis::SetMaxDigits(2);')    
     gStyle.SetFrameBorderMode(0)
     gStyle.SetFrameFillColor(0)
     gStyle.SetCanvasBorderMode(0)

### 2014-12-12 python/variable_s.py

@@ -4,10 +4,10 @@ import ROOT
 import numpy as np
 import sys
 from styleit import gstyle
-
-ROOT.gROOT.ProcessLine("TGaxis::SetMaxDigits(2);")
+from ROOT import TGaxis
 
 gstyle()
+TGaxis.SetMaxDigits(2)
 
 data = np.loadtxt(sys.argv[1])
 tm, tr, pm, pr, dt, pvx0, tvx0, ip, k, eta, L, ms, fvxt, fvyt, fvt, fvxp, fvyp, fvp, tts = data.T
@@ -17,7 +17,7 @@ vfp_vs_ip = ROOT.TGraph()
 vft_vs_ip = ROOT.TGraph()
 el_vs_ip  = ROOT.TGraph()
 
-dx_vs_ip.SetTitle(';s;#frac{#Delta x_{max}}{r_{t}}')
+dx_vs_ip.SetTitle(';s;#frac{#Delta x_{max}}{r_{t}} #times 10')
 vfp_vs_ip.SetTitle(';s;Projectile v_{f}')
 vft_vs_ip.SetTitle(';s;Target v_{f}')
 el_vs_ip.SetTitle(';s;Energy Loss')
@@ -26,7 +26,7 @@ i = 0
 for iip, ipvx0, ims, ifvt, ifvp in zip(ip,pvx0,ms,fvt,fvp):
     if ifvp > 4.8:
         continue
-    dx_vs_ip.SetPoint(i,iip,(tr[0]+pr[0]-ims)/tr[0])
+    dx_vs_ip.SetPoint(i,iip,(tr[0]+pr[0]-ims)/tr[0]*10)
     vfp_vs_ip.SetPoint(i,iip,ifvp)
     vft_vs_ip.SetPoint(i,iip,ifvt)
     el_vs_ip.SetPoint(i,iip,0.5*pm[0]*ipvx0*ipvx0-(0.5*pm[0]*ifvp*ifvp+0.5*tm[0]*ifvt*ifvt))
@@ -40,6 +40,7 @@ vfp_vs_ip.SetMarkerStyle(7)
 vfp_vs_ip.SetMarkerColor(ROOT.kRed)
 
 c1 = ROOT.TCanvas()
+dx_vs_ip.GetYaxis().SetTitleOffset(.95)
 dx_vs_ip.Draw('AP')
 c2 = ROOT.TCanvas()
 el_vs_ip.Draw('AP')

### 2014-12-12 paper/paper.tex
edited paper

@@
 To ensure that $\Delta t$ is not set too large the code checks each masses change in position at every time step.
-If the change in position is larger than 1\% of the masses radius a warning is generated and the simulation is re-run with a smaller $\Delta t$
+If the change in position is larger than 1\% of the masses radius a warning is generated and the simulation is re-run with a smaller $\Delta t$.
+Throughout the rest of this paper SI units are assumed where none are given.
 \begin{equation}\label{eq:energy}
@@
 \subsection{Simulation Performance}
+\subsubsection{Default Configuration}
 One of the first tasks was to validate the simulation framework using a system where the physics was simple and easy to intuitively predict.
-This system uses a stationary target of radius units 2, with a projectile of radius units 1 incoming at velocity units 5 with an impact parameter of 1 unit.
+This system uses a stationary target of radius 2, with a projectile of radius 1 incoming at velocity 5 with an impact parameter of 1.
 The objects have equal density.
-We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ force constant.
-First we visualize the track points for each objects tracjectory while they are in contact with each other.
-We show this visualization in Figure~\ref{fig:tracks_default}.
+We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ spring constant.
+To begin to get an understanding of the collision we first plot each objects center of mass tracjectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}).
+The projectile rebounds off the target sending it off at a slow velocity in the oposite direction will the systems center of mass steadly moves in a straight line.
 \begin{figure}[h!]
@@
 The collections of points (which form a continuous line) show the position of the center of each object at each time step while the objects are in contact.
-(R) The state of the system when the objects are at a minimum separation (maximum $\Delta x$ from equilibrium).}
+(R) The state of the system when the objects are at a minimum separation i.e.
+maximum $\Delta x$ from equilibrium.}
                   \label{fig:tracks_default}
 \end{figure}
-We also check for kinematic trends to be physically sound for the given initial conditions and parameters of the system.
+
+discuss energy here
+
 \begin{figure}
@@
 \end{figure}
+
+\subsubsection{c6 Equal Masses, Zero Momentum}
+the
+
+\subsubsection{c7}
+the
 

### 2014-12-12 paper/paper.tex
updated c7 plots

@@
 \end{equation}
-
 \begin{equation}\label{eq:velocity}
@@
 We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ spring constant.
-To begin to get an understanding of the collision we first plot each objects center of mass tracjectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}).
+To begin to get an understanding of the collision we first plot each objects center of mass trajectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}).
 The projectile rebounds off the target sending it off at a slow velocity in the oposite direction will the systems center of mass steadly moves in a straight line.
@@
 
-discuss energy here
-
+Potential and kinetic energy of the system is tracked throughout the simulation steps giving us the ability to moniter total energy conservation.
+It also allows us to visualize the flow of energy throughout the system.
+For the default configuration, that energy flow is shown in Figure~\ref{fig:energy_default}.
+It can be seen that the total energy trend is not completely constant.
+This is believed to be from the approximate quality of the simulation using finite time steps.
+The discrepancy is very small.
 \begin{figure}
@@
   \caption{Trends for different energies in the system: object and total kinetic energies, potential energy, and the total energy of the system.}
+  \label{fig:energy_default}
 \end{figure}
 
-\subsubsection{c6 Equal Masses, Zero Momentum}
-the
+\subsubsection{Equal Masses, Zero Momentum}
+Another system we investigated for validation was a system with two identical objects colliding with each other at equal but opposite velocities.
+In this system the objects have equal density with a radius of 1 and the initial velocities are $5$ and $-5$, respectively.
+The observed behavior is present in Figures~\ref{fig:tracks_c6}~and~\ref{fig:vx_c6}.
+The trends for the motions of the objects are as expected, specifically we were looking for antisymmetric velocity trends and constant system center of mass momentum.
+\begin{figure}[h!]
+  \includegraphics[width=.45\textwidth]{plots/out_c6/x_vs_y_with_ellipse.pdf}
+  \includegraphics[width=.45\textwidth]{plots/out_c6/x_vs_y_with_ellipse_MS.pdf}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+                  \caption{(L) Object initial state, with tracks points (R) Objects at minimum separation, with track points}
+                  \label{fig:tracks_c6}
+\end{figure}
+\begin{figure}[h!]
+  \includegraphics[width=.45\textwidth]{plots/out_c6/vx_vs_t.pdf}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+                  \caption{The velocity in the $x$ direction for both objects.
+The trend shows that the objects slow as the come together, come to rest, and move off in opposite directions again.
+As expected the system's center of mass velocity is zero.}
+                  \label{fig:vx_c6}
+\end{figure}
 
-\subsubsection{c7}
+\subsubsection{Large fast moving target on slow moving projectile}
 the

### 2014-12-12 main.cpp

@@ -111,7 +111,7 @@ int main(int argc, char *argv[])
     else if ( my_case == 6 )
       K = 1000.0, target_radius = 1.00, projectile_radius = 1.00, target_mass = 3.00, projectile_mass = 3.00, impact_parameter = 0.00, projectile_vx0 = 5.00, target_vx0 = -5.00;
     else if ( my_case == 7 )
-      K = 1000.0, target_radius = 3.00, projectile_radius = 1.00, target_mass = 15.00, projectile_mass = 1.00, impact_parameter = 0.00, projectile_vx0 = 1.00, target_vx0 = -5.00;
+      K = 1000.0, target_radius = 3.00, projectile_radius = 1.00, target_mass = 30.00, projectile_mass = 1.00, impact_parameter = 0.00, projectile_vx0 = 8.00, target_vx0 = -2.00;
     else
       std::cout << "case parameter out of bounds, using defaults" << std::endl;
   }

### 2014-12-13 paper/paper.tex
committing current paper version

@@
 The objects have equal density.
-We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ spring constant.
+We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ force constant.
 To begin to get an understanding of the collision we first plot each objects center of mass trajectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}).
@@
 
-\subsubsection{Equal Masses, Zero Momentum}
+\subsubsection{Equal Masses, zero net momentum}
 Another system we investigated for validation was a system with two identical objects colliding with each other at equal but opposite velocities.
-In this system the objects have equal density with a radius of 1 and the initial velocities are $5$ and $-5$, respectively.
+In this system the objects have equal density with a radius of 1 and the initial velocities are $5$ and $-5$, respectively; the force constant was $k = 1000$ and $\lambda = 1$.
 The observed behavior is present in Figures~\ref{fig:tracks_c6}~and~\ref{fig:vx_c6}.
@@
 
-\subsubsection{Large fast moving target on slow moving projectile}
-the
-
+\subsubsection{Large, slow moving target with small, fast projectile}
+The final validation system we investigated was made up of a target with mass 30 and radius 3 moving with velocity $-2$ and a projectile with mass 1 and radius 1 moving with velocity 8; the force constant was $k = 1000$ and $\lambda = 1$.
+The impact parameter was set to 0.
+For this system we were looking for large momentum transfer to the projectile (essentially being quickly turned around by the slightly effected target).
+Figure~\ref{fig:tracks_c7} shows the object trajectories.
+Figure~\ref{fig:vx_c7} shows the horizontal velocities for the system.
+As expectd, the large and slow target is slightly effected and its motion remains in the same direction, while the small and fast projectile is deflected against the target and moves away at a faster velocity compared to its incoming velocity.
+\begin{figure}[h!]
+  \includegraphics[width=.45\textwidth]{plots/out_c7/x_vs_y_with_ellipse.pdf}
+  \includegraphics[width=.45\textwidth]{plots/out_c7/x_vs_y_with_ellipse_MS.pdf}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+                  \caption{(L) Object initial state, with tracks points (R) Objects at minimum separation, with track points}
+                  \label{fig:tracks_c7}
+\end{figure}
+\begin{figure}[h!]
+  \includegraphics[width=.45\textwidth]{plots/out_c7/vx_vs_t.pdf}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+                  \caption{The velocity trend for each object and the center of mass.
+The velocity of the target is slightly changed, and stays in the same direction (to the left), while the incoming projectile is quickly turned around and given a larger velocity in the opposite direction compared to where it came out.}
+                  \label{fig:vx_c7}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% trend studies %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Initial Velocity Studies}
-The
+Many systems were simulated where we varied the initial velocity.
+Figure~\ref{fig:changing_pvinit1}(L) shows the maximum displacement from the ``spring'' equilibrium position versus initial velocity of the projectile.
+All of these systems were consistent in other parameters.
+This includes target radius and mass of 2, projectile radius of 0.25 and radius of 1 (equal densities).
+The impact parameter was 1, $\eta = 0$, and $\lambda = 1$.
+Figure~\ref{fig:changing_pvinit1}(R) shows the energy loss per initial energy for the interaction.
+A perfect system would have a flat line at zero, but we are using finite time steps with this computational approximaton, therefore we have a slight gain in energy for low initial velocities.
+Figure~\ref{fig:energy_default} shows a a small increase in total energy for that particular system.
+\begin{figure}[h!]
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/dxmax_vs_pvinit.pdf}
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/Eloss_vs_pvinit.pdf}
+  \caption{(L) The maximum displacement from equilibrium divided by the target radius vs.
+the initial velocity of the projectile.
+(R) The energy loss divided by the initial energy of the system vs.
+initial velocity of the projectile.}
+  \label{fig:changing_pvinit1}
+\end{figure}
 
 \subsection{Impact Parameter Studies}
-The
+Many systems were simulated where we varied the impact parameter. Figures~\ref{fig:changing_s1}~and~\ref{fig:changing_s2}.
+\begin{figure}[h!]
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/Eloss_vs_s.pdf}
+  \caption{The energy loss divided by the initial energy of the system vs. impact parameters.}
+  \label{fig:changing_s1}  
+\end{figure}
+\begin{figure}[h!]
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/pvf_vs_s.pdf}
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/tvf_vs_s.pdf}
+  \caption{(L) The projectile final velocity vs. impact parameters. (R) The target final velocity vs. impact parameters.}
+  \label{fig:changing_s2}
+\end{figure}
 
 \subsection{Force Power Law Dependence}
-The
+Many systems were simulated where we varied the force power law parameter $\lambda$. Figure~\ref{fig:changing_lambda}.
+\begin{figure}[h!]
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/dxmax_vs_lambda.pdf}
+  \caption{lambda}
+  \label{fig:changing_lambda}
+\end{figure}
 
 \subsection{Energy Dissipation Studies}
-The
+Many systems were simulated where we varied the energy dissipation parameter $\eta$. Figure~\ref{fig:changing_eta}.
+\begin{figure}[h!]
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/dxmax_vs_eta.pdf}
+  \includegraphics[width=.45\linewidth]{plots/trend_plots/Eloss_vs_eta.pdf}
+  \caption{eta}
+  \label{fig:changing_eta}
+\end{figure}
 
@@
 \clearpage
-\begin{appendices}
-  \singlespacing
-  \section{main.cpp Physics Loop} \label{sec:main.cpp}
-  \lstinputlisting[firstline=170, lastline=246]{../main.cpp}% lots of pages, only uncomment when you want it
+%\begin{appendices}
+%  \singlespacing
+%  \section{main.cpp Physics Loop} \label{sec:main.cpp}
+%  \lstinputlisting[firstline=170, lastline=246]{../main.cpp}% lots of pages, only uncomment when you want it
 
-\end{appendices}
+%\end{appendices}
 

### 2014-12-13 paper/paper.tex
paper upping

@@
 The impact parameter was 1, $\eta = 0$, and $\lambda = 1$.
-Figure~\ref{fig:changing_pvinit1}(R) shows the energy loss per initial energy for the interaction.
+Figure~\ref{fig:changing_pvinit1}(R) shows the energy loss per initial energy for the sample of systems.
 A perfect system would have a flat line at zero, but we are using finite time steps with this computational approximaton, therefore we have a slight gain in energy for low initial velocities.
@@
 \subsection{Impact Parameter Studies}
-Many systems were simulated where we varied the impact parameter. Figures~\ref{fig:changing_s1}~and~\ref{fig:changing_s2}.
+Many systems were simulated where we varied the impact parameter.
+Similar to the previous study, we again look at the trend of maximum displacement from equilibrium versus the varying parameter, which is now the impact parameter.
+During the generation of this sample, all other paramters were constant: target radius and mass of 2, projectile radius of 0.25 and radius of 1 (equal densities).
+The projectile initial velocity was 5, $\eta = 0$, and $\lambda = 1$.
+The trend shows that as the collision point becomes more off-center with respect to the target, the smaller the spring action between the two objects.
 \begin{figure}[h!]
   \includegraphics[width=.45\linewidth]{plots/trend_plots/Eloss_vs_s.pdf}
-  \caption{The energy loss divided by the initial energy of the system vs. impact parameters.}
+  \caption{The maximum displacement from equilibrium divided by the target radius vs. impact parameters.}
   \label{fig:changing_s1}  
 \end{figure}
+Figure~\ref{fig:changing_s2} shows the trend of the final velocities of the objects versus the impact parameter.
 \begin{figure}[h!]

### 2014-12-13 paper/paper.tex
added emails
yayaya

@@
 
-\subsubsection{Equal Masses, zero net momentum}
+\subsubsection{Equal masses, zero net momentum}
 Another system we investigated for validation was a system with two identical objects colliding with each other at equal but opposite velocities.
@@
   \includegraphics[width=.45\linewidth]{plots/trend_plots/Eloss_vs_pvinit.pdf}
-  \caption{(L) The maximum displacement from equilibrium divided by the target radius vs.
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+                  \caption{(L) The maximum displacement from equilibrium per target radius vs.
 the initial velocity of the projectile.
@@
   \includegraphics[width=.45\linewidth]{plots/trend_plots/Eloss_vs_s.pdf}
-  \caption{The maximum displacement from equilibrium divided by the target radius vs. impact parameters.}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+                  \caption{The maximum displacement from equilibrium per the target radius vs. impact parameters.}
                   \label{fig:changing_s1}  
@@
 Figure~\ref{fig:changing_s2} shows the trend of the final velocities of the objects versus the impact parameter.
+We find that for more head on collisions, the projectile transfers more momentum to the target, while for large impact parameters the projectile keeps most of its momentum.
 \begin{figure}[h!]
@@
   \includegraphics[width=.45\linewidth]{plots/trend_plots/tvf_vs_s.pdf}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
                   \caption{(L) The projectile final velocity vs. impact parameters. (R) The target final velocity vs. impact parameters.}
@@
 \subsection{Force Power Law Dependence}
-Many systems were simulated where we varied the force power law parameter $\lambda$. Figure~\ref{fig:changing_lambda}.
+Many systems were simulated where we varied the force power law parameter $\lambda$.
+We varied $\lambda$ from $1/2$ to $3$, which corresponds to a force law depending on the square root of the displacement up to depending on the cube of the displacement.
+Figure~\ref{fig:changing_lambda} shows this sample of maximum displacement from equilibrium versus the force law power.
+The trend has a positive slope throughout.
+This is unexpected, as we thought a larger $\lambda$ would correspond to a stronger restoring force between the objects, causing a smaller deformation.
+We now believe this is because all of the displacement values, $\Delta x$, are less than 1.
 \begin{figure}[h!]
   \includegraphics[width=.45\linewidth]{plots/trend_plots/dxmax_vs_lambda.pdf}
-  \caption{lambda}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+                  \caption{The maximum displacement from equilibrium per target radius vs. $\lambda$}
                   \label{fig:changing_lambda}
@@
   \includegraphics[width=.45\linewidth]{plots/trend_plots/Eloss_vs_eta.pdf}
+                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
+
                   \caption{eta}

### 2014-12-13 paper/paper.tex
asdfasdf
sync up

@@
 \title{Modeling Two Body Collisions with Spring Potential Interactions}
-\author{Matthew \textsc{Epland}, Douglas \textsc{Davis}}
+\author{Matthew \textsc{Epland}}
+\email{mbe9@phy.duke.edu}
+\author{ Douglas \textsc{Davis}}
+\email{drd25@phy.duke.edu}
+%\href{mailto:my_address@wikibooks.org}{my\_address@wikibooks.org}
 \affiliation{Department of Physics, Duke University}
@@
 The impact parameter was 1, $\eta = 0$, and $\lambda = 1$.
+The asymptote at $\Delta x_{\text{max}}/r_t$ at 1 shows that as the initial velocity of the projectile increases, the impact reaches the radius of the target.
 Figure~\ref{fig:changing_pvinit1}(R) shows the energy loss per initial energy for the sample of systems.
@@
 During the generation of this sample, all other paramters were constant: target radius and mass of 2, projectile radius of 0.25 and radius of 1 (equal densities).
-The projectile initial velocity was 5, $\eta = 0$, and $\lambda = 1$.
+The projectile initial velocity was 5, $\eta = 0$, $\Delta t = 0.0001$, and $\lambda = 1$.
 The trend shows that as the collision point becomes more off-center with respect to the target, the smaller the spring action between the two objects.
@@
 We varied $\lambda$ from $1/2$ to $3$, which corresponds to a force law depending on the square root of the displacement up to depending on the cube of the displacement.
+The other parameters for all simulated systems: target radius and mass of 2, projectile radius of 0.25 and radius of 1 (again, equal densities).
+The projectile velocity was again 5 and $\eta = 0$.
 Figure~\ref{fig:changing_lambda} shows this sample of maximum displacement from equilibrium versus the force law power.
@@
 \subsection{Energy Dissipation Studies}
-Many systems were simulated where we varied the energy dissipation parameter $\eta$. Figure~\ref{fig:changing_eta}.
-\begin{figure}[h!]
+Many systems were simulated where we varied the energy dissipation parameter $\eta$.
+Other system parameters included: target radius and mass of 2, projectile radius of 0.25 and radius of 1 (again, equal densities).
+The projectile velocity was again 5 and $\lambda = 0$.
+Figure~\ref{fig:changing_eta}(L) shows the trend for the maximum displacement from equilibrium versus the energy dissipation parameter.
+This shows that the larger the energy dissipation parameter, the smaller the deformation between the projectile and the target.
+Figure~\ref{fig:changing_eta}(R) shows the trend for the energy loss per initial energy versus energy dissipation parameter.
+We see in this trend that at a certain $\eta$, the final total energy of the system approaches zero.
+\begin{figure}
   \includegraphics[width=.45\linewidth]{plots/trend_plots/dxmax_vs_eta.pdf}
@@
                   {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
-
-                  \caption{eta}
+                  \caption{(L) the maximum displacement from equilibrium per target radius vs. $\eta$. (R) The energy loss per initial energy vs. $\eta$.}
                   \label{fig:changing_eta}

### 2014-12-13 paper/paper.tex

@@
 We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ force constant.
+$\Delta t = 0.001$ was found to give sufficent precision for most studies and is the default $\Delta t$ value for all simulations unless otherwise noted.
 To begin to get an understanding of the collision we first plot each objects center of mass trajectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}).
-The projectile rebounds off the target sending it off at a slow velocity in the oposite direction will the systems center of mass steadly moves in a straight line.
+The projectile rebounds off the target sending it off at a slow velocity in the oposite direction while the systems center of mass moves steadly in a straight line.
 \begin{figure}[h!]

### 2014-12-13 paper/paper.tex
finished conclusionsgit add paper/paper.tex git add paper/paper.tex

--- 2014-12-13 paper/paper.tex
@@
 \end{figure}
-\begin{figure}[h!]
+\begin{figure}[floatfix]
   \includegraphics[width=.45\textwidth]{plots/out_c7/vx_vs_t.pdf}
@@
 Figure~\ref{fig:energy_default} shows a a small increase in total energy for that particular system.
-\begin{figure}[h!]
+\begin{figure}[floatfix]
   \includegraphics[width=.45\linewidth]{plots/trend_plots/dxmax_vs_pvinit.pdf}
@@
 \section{Conclusion}
-The
+The simulation developed in this study performed well in general.
+It was sucessfully used to investigate a variety of two-body collisions.
+The three validation systems all displayed the expected behavior, specifically momentum conservation, as seen in a constant velocity system center of mass, and the conservation of energy.
+The simulated total energy of the systems did vary slightly, usually increasing over time, but it is a relativly small effect.
+Having a more developed simulation with potentially smaller time steps and higher floating point precision would likely reduce these total energy fluctuations.
+
+The final velocity and maximum displacement results when varying the projectiles initial velocity and the inpact parameter largely matched our expectations.
+However, while varying the force power law, $\lambda$, the maximum displacement decreased with increasing $\lambda$ which was unexpected.
+We believe that this inverse relationship beween $\lambda$ and $\Delta x_{max}$ is due to all of our simulations having $\Delta x \leq 1$, additional studies could modify the initial parameters to investigate this theory further in the case where $\Delta x \geq 1$.
+When we included a non-zero energy disipation coefficent, $\eta$ we observed a very rapid decay of the total energy and hence final velocity.
+This general behvior was expected, but not to the degree seen.
+An improved method of including energy disipation for future simulations would be to normalize the energy lost per time step to $\Delta t$ by altering $\left(1-\eta\right)~\rightarrow~\left(1-\eta\right)\Delta t$ so that the energy loss per unit time is independent of the number of time steps used to simulate that unit time.
 
@@
 \clearpage
-%\begin{appendices}
-%  \singlespacing
-%  \section{main.cpp Physics Loop} \label{sec:main.cpp}
-%  \lstinputlisting[firstline=170, lastline=246]{../main.cpp}% lots of pages, only uncomment when you want it
+\begin{appendices}
+  \singlespacing
+  \section{main.cpp Physics Loop} \label{sec:main.cpp}
+  \lstinputlisting[firstline=170, lastline=246]{../main.cpp}% lots of pages, only uncomment when you want it
 
-%\end{appendices}
+\end{appendices}
 

### 2014-12-13 paper/paper.tex
slight paper changes

@@
 One of the masses, the target $m_{1}$, may be at rest initially, though we also allow it to have an initial closing velocity in some studies.
-For continence we pick our coordinate system such that all the initial velocities lie along $\hat{x}$ and the target is on the $\hat{y}$ axis, $y_{1}(t=0)=0$ (Figure~\ref{fig:schematic}).
+For convenience we pick our coordinate system such that all the initial velocities lie along $\hat{x}$ and the target is on the $\hat{y}$ axis, $y_{1}(t=0)=0$ (Figure~\ref{fig:schematic}).
 
@@
 However, while varying the force power law, $\lambda$, the maximum displacement decreased with increasing $\lambda$ which was unexpected.
-We believe that this inverse relationship beween $\lambda$ and $\Delta x_{max}$ is due to all of our simulations having $\Delta x \leq 1$, additional studies could modify the initial parameters to investigate this theory further in the case where $\Delta x \geq 1$.
+We believe that this inverse relationship beween $\lambda$ and $\Delta x_{\text{max}}$ is due to all of our simulations having $\Delta x \leq 1$, additional studies could modify the initial parameters to investigate this theory further in the case where $\Delta x \geq 1$.
 When we included a non-zero energy disipation coefficent, $\eta$ we observed a very rapid decay of the total energy and hence final velocity.

### 2014-12-13 paper/paper.tex
added ref for nonlinear const
proofreading1

@@
   This paper describes a computational study of two body collisions where the dynamics of the bodies are governed by a Hooke's Law type force at the interaction points.
-We investigate a number of scenarios which involve both a stationary target mass which is stuck by a projectile mass with some horizontal velocity in a two dimensional plane, as well as scenarios where both masses are moving in towards each other.
+We investigate a number of scenarios involving a stationary target mass that is stuck by a projectile mass with some horizontal velocity in a two dimensional plane, as well as scenarios where both masses are moving in towards each other.
 The masses trajectories are determined from a simulation software package, written by the authors, that models the force between the masses as they interact with each other based on the initial kinematic state of the system.
-Specific attention was given to the systems behavior with different initial projectile velocities, impact parameters, energy loss rates and power dependence in the force law.
+Specific attention was given to the systems behavior with different initial projectile velocities, impact parameters, energy loss rates and power dependence in the force law itself.
 \end{abstract}\maketitle
@@
 
-In order to rapidly investigate the many possible variations of this seemingly simple two body collision a software simulation was chosen over attempting to solve each variation analytically.
+In order to rapidly investigate the many possible variations of this seemingly simple two body collision a software simulation was chosen over attempting to solve each variation of the problem analytically.
 Written in \texttt{C++} and using some of the \texttt{ROOT}~\cite{ref_root} particle physics analysis libraries the simulation code at its core operates by iteratively calculating the object's change in position and velocity during a small time step, $\Delta t$, during which the acceleration is assumed to be constant.

### 2014-12-13 paper/paper.tex
almost done

@@
 Setting $\lambda = 1$ results in the familiar Hook's Law spring force, but by including the $\lambda$ power dependence we are able to study a wider array of collisions, particularly those where the masses deform enough that the normal force between them becomes nonlinear.
+It is possible, and sometimes even desirable, to design a system with $\lambda \neq 1$~\cite{ref_spring}.
 As the masses deform and push against each other some of the mechanical energy of the system may be lost to internal degrees of freedom, such as heat.
@@
 One of the masses, the target $m_{1}$, may be at rest initially, though we also allow it to have an initial closing velocity in some studies.
-For convenience we pick our coordinate system such that all the initial velocities lie along $\hat{x}$ and the target is on the $\hat{y}$ axis, $y_{1}(t=0)=0$ (Figure~\ref{fig:schematic}).
+For convenience we pick our coordinate system such that all the initial velocities lie along $\hat{\mathbf{x}}$ and the target is on the $\hat{\mathbf{y}}$ axis, $y_{1}(t=0)=0$ (Figure~\ref{fig:schematic}).
 
@@
   \centering
-  \includegraphics[width=.75\textwidth]{plots/cj_diag.pdf}
+  \includegraphics[width=.70\textwidth]{plots/cj_diag.pdf}
 	          {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
@@
 
-In addition to the position and velocity of the masses we also calculate their kinetic energies and the potential energy stored in the deformed bodies, e.g.
-spring \eqref{eq:energy}.
+In addition to the position and velocity of the masses we also calculate their kinetic energies and the potential energy stored in the deformed bodies \eqref{eq:energy}.
 The force is conservative, so $\mathbf{F} = - \nabla V \rightarrow V = \int \left|F\right| d\left(\Delta x\right)$.
@@
 The collections of points (which form a continuous line) show the position of the center of each object at each time step while the objects are in contact.
-(R) The state of the system when the objects are at a minimum separation i.e.
+(R) The state of the system when the objects center of masses are at a minimum separation i.e.
 maximum $\Delta x$ from equilibrium.}
@@
 For the default configuration, that energy flow is shown in Figure~\ref{fig:energy_default}.
-It can be seen that the total energy trend is not completely constant.
+It can be seen that the total energy trend is not completely constant, but the discrepancy is very small.
 This is believed to be from the approximate quality of the simulation using finite time steps.
-The discrepancy is very small.
 \begin{figure}
@@
 Another system we investigated for validation was a system with two identical objects colliding with each other at equal but opposite velocities.
-In this system the objects have equal density with a radius of 1 and the initial velocities are $5$ and $-5$, respectively; the force constant was $k = 1000$ and $\lambda = 1$.
-The observed behavior is present in Figures~\ref{fig:tracks_c6}~and~\ref{fig:vx_c6}.
+In this system the objects have equal density with a radius of 1 and the initial velocities are $5$ and $-5$, respectively; the force constant was $k = 1000$, and $\lambda = 1$ (Figures~\ref{fig:tracks_c6}~and~\ref{fig:vx_c6}).
 The trends for the motions of the objects are as expected, specifically we were looking for antisymmetric velocity trends and constant system center of mass momentum.
@@
                   {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
-                  \caption{(L) Object initial state, with tracks points (R) Objects at minimum separation, with track points}
+                  \caption{Track points overlayed with the initial state (L), and objects at minimum separation (R).}
                   \label{fig:tracks_c6}
@@
                   {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
-                  \caption{The velocity in the $x$ direction for both objects.
-The trend shows that the objects slow as the come together, come to rest, and move off in opposite directions again.
+                  \caption{The velocity along the $\hat{\mathbf{x}}$ axis for both objects.
+The trend shows that the objects slow as they come together, stop, and then move off in opposite directions again.
 As expected the system's center of mass velocity is zero.}
@@
 The impact parameter was set to 0.
-For this system we were looking for large momentum transfer to the projectile (essentially being quickly turned around by the slightly effected target).
-Figure~\ref{fig:tracks_c7} shows the object trajectories.
-Figure~\ref{fig:vx_c7} shows the horizontal velocities for the system.
-As expectd, the large and slow target is slightly effected and its motion remains in the same direction, while the small and fast projectile is deflected against the target and moves away at a faster velocity compared to its incoming velocity.
+For this system we were looking for large momentum transfer to the projectile, essentially being quickly turned around by the much more massive target which is only slightly affected.
+The object trajectories (Figure~\ref{fig:tracks_c7}) and $\hat{\mathbf{x}}$ velocities for the system (Figure~\ref{fig:vx_c7}) were again plotted.
+As expected, the large, slow moving target is slightly effected and its motion remains in the same direction, while the small and fast projectile is deflected against the target and leaves the collision at a higher velocity than its incoming velocity.
 \begin{figure}[h!]
@@
                   {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
-                  \caption{(L) Object initial state, with tracks points (R) Objects at minimum separation, with track points}
+                  \caption{Track points overlayed with the initial state (L), and objects at minimum separation (R).}
                   \label{fig:tracks_c7}
@@
                   \caption{The velocity trend for each object and the center of mass.
-The velocity of the target is slightly changed, and stays in the same direction (to the left), while the incoming projectile is quickly turned around and given a larger velocity in the opposite direction compared to where it came out.}
+The velocity of the target is slightly changed, and stays in the same direction (to the left), while the incoming projectile is quickly turned around and given a larger velocity in the opposite direction compared to its initial velocity.}
                   \label{fig:vx_c7}
@@
   \section{Bibliography}
+\bibitem{ref_spring}
+  Chris Cortopassi and Ongi Englander, Nonlinear Springs for Increasing the Maximum Stable Deflection of MEMS Electrostatic Gap Closing Actuators
 \bibitem{ref_root}
@@
 See also http://root.cern.ch/.
-
 \end{thebibliography}

### 2014-12-13 paper/paper.tex
spelling

@@
 We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ force constant.
-$\Delta t = 0.001$ was found to give sufficent precision for most studies and is the default $\Delta t$ value for all simulations unless otherwise noted.
+$\Delta t = 0.001$ was found to give sufficient precision for most studies and is the default $\Delta t$ value for all simulations unless otherwise noted.
 To begin to get an understanding of the collision we first plot each objects center of mass trajectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}).
-The projectile rebounds off the target sending it off at a slow velocity in the oposite direction while the systems center of mass moves steadly in a straight line.
+The projectile rebounds off the target sending it off at a slow velocity in the opposite direction while the systems center of mass moves steadily in a straight line.
 \begin{figure}[h!]
@@
 
-Potential and kinetic energy of the system is tracked throughout the simulation steps giving us the ability to moniter total energy conservation.
+Potential and kinetic energy of the system is tracked throughout the simulation steps giving us the ability to monitor total energy conservation.
 It also allows us to visualize the flow of energy throughout the system.
@@
                   {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
-                  \caption{Track points overlayed with the initial state (L), and objects at minimum separation (R).}
+                  \caption{Track points overlaid with the initial state (L), and objects at minimum separation (R).}
                   \label{fig:tracks_c6}
@@
 Figure~\ref{fig:changing_pvinit1}(R) shows the energy loss per initial energy for the sample of systems.
-A perfect system would have a flat line at zero, but we are using finite time steps with this computational approximaton, therefore we have a slight gain in energy for low initial velocities.
-Figure~\ref{fig:energy_default} shows a a small increase in total energy for that particular system.
+A perfect system would have a flat line at zero, but we are using finite time steps with this computational approximation, therefore we have a slight gain in energy for low initial velocities.
+Figure~\ref{fig:energy_default} shows a small increase in total energy for that particular system.
 \begin{figure}[floatfix]
@@
 Similar to the previous study, we again look at the trend of maximum displacement from equilibrium versus the varying parameter, which is now the impact parameter.
-During the generation of this sample, all other paramters were constant: target radius and mass of 2, projectile radius of 0.25 and radius of 1 (equal densities).
+During the generation of this sample, all other parameters were constant: target radius and mass of 2, projectile radius of 0.25 and radius of 1 (equal densities).
 The projectile initial velocity was 5, $\eta = 0$, $\Delta t = 0.0001$, and $\lambda = 1$.
@@
 The simulation developed in this study performed well in general.
-It was sucessfully used to investigate a variety of two-body collisions.
+It was successfully used to investigate a variety of two-body collisions.
 The three validation systems all displayed the expected behavior, specifically momentum conservation, as seen in a constant velocity system center of mass, and the conservation of energy.
-The simulated total energy of the systems did vary slightly, usually increasing over time, but it is a relativly small effect.
+The simulated total energy of the systems did vary slightly, usually increasing over time, but it is a relatively small effect.
 Having a more developed simulation with potentially smaller time steps and higher floating point precision would likely reduce these total energy fluctuations.
 
-The final velocity and maximum displacement results when varying the projectiles initial velocity and the inpact parameter largely matched our expectations.
+The final velocity and maximum displacement results when varying the projectiles initial velocity and the impact parameter largely matched our expectations.
 However, while varying the force power law, $\lambda$, the maximum displacement decreased with increasing $\lambda$ which was unexpected.
-We believe that this inverse relationship beween $\lambda$ and $\Delta x_{\text{max}}$ is due to all of our simulations having $\Delta x \leq 1$, additional studies could modify the initial parameters to investigate this theory further in the case where $\Delta x \geq 1$.
-When we included a non-zero energy disipation coefficent, $\eta$ we observed a very rapid decay of the total energy and hence final velocity.
-This general behvior was expected, but not to the degree seen.
-An improved method of including energy disipation for future simulations would be to normalize the energy lost per time step to $\Delta t$ by altering $\left(1-\eta\right)~\rightarrow~\left(1-\eta\right)\Delta t$ so that the energy loss per unit time is independent of the number of time steps used to simulate that unit time.
+We believe that this inverse relationship between $\lambda$ and $\Delta x_{\text{max}}$ is due to all of our simulations having $\Delta x \leq 1$, additional studies could modify the initial parameters to investigate this theory further in the case where $\Delta x \geq 1$.
+When we included a non-zero energy dissipation coefficient, $\eta$ we observed a very rapid decay of the total energy and hence final velocity.
+This general behavior was expected, but not to the degree seen.
+An improved method of including energy dissipation for future simulations would be to normalize the energy lost per time step to $\Delta t$ by altering $\left(1-\eta\right)~\rightarrow~\left(1-\eta\right)\Delta t$ so that the energy loss per unit time is independent of the number of time steps used to simulate that unit time.
 
